\documentclass{proc}

\title{1100 Week 30 Onward}
%\usepackage{hyperref}
\usepackage{soul}
\usepackage{xcolor}
\definecolor{brickred}{RGB}{183,50,57}
\definecolor{gold}{RGB}{170,108,57}
%\hyphenpenalty=10000
%\exhyphenpenalty=10000


	\iffalse

\newpage
\setcounter{section}{weeknum}
\setcounter{subsection}{0}


\subsection{}
\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\newpage
\subsection{}
\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\newpage
\subsection{}
\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\newpage
\subsection{}
\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

\subsubsection{\textcolor{brickred}{} ()}

\textcolor{gold}{ ""}

	\fi

\begin{document}
	%\maketitle
	\setcounter{section}{30}
	%\setcounter{subsection}{1}
	%\section*{}
		\subsection{}
			\subsubsection{\textcolor{brickred}{extinct} (adj)}
			 no longer in existence.
			 \textcolor{gold}{"an extinct language"
			 "the now extinct life aboard a 
			 steamer on the Mississippi River"}
			 
			 \subsubsection{\textcolor{brickred}{idyllic} (adj)}
			 (especially of a time or place) like an idyll; extremely happy, peaceful, or picturesque. blissful, halcyon
			 \textcolor{gold}{"Twain recalls the idyllic times when man 
			 was not in such a great rush to get from one place to another."
			 "an attractive hotel in an idyllic setting"
			 "the idyllic life in the country."
			 "the rural \textbf{idyll} remains strongly evocative in most industrialized societies"}
			 
			 \subsubsection{\textcolor{brickred}{galvanize} (v)}
			 shock or excite (someone) into taking action.
			 \textcolor{gold}{"the urgency of his voice galvanized them \textbf{into} action"
			 "Environmentalists try to galvanize large numbers of people to pressure politicians into passing conservation legislation."}

			 
			 \subsubsection{\textcolor{brickred}{encumbrance} (n)}
			 a burden or impediment. hindrance, obstruction
			 \textcolor{gold}{"the horse raised its hind leg as if to rid itself of an encumbrance"
			 "every encumbrance that might slow the passage was removed to lighten their boats."
			 "It is amazing how \textbf{lithe} football players can be, despite the encumbrance of the
			 safety features of their uniforms."}
			 
			 \subsubsection{\textcolor{brickred}{gaudy} (adj)}
			 extravagantly bright or showy, typically so as to be tasteless. flashy
			 \textcolor{gold}{"silver bows and gaudy ribbons"
			 "a gaudy dress"
			 "Twain writes 
			 of one captain who scraped the paint from the gaudy figure 
			 that hung between the chimneys of his steamer."}\\
			 \\
			 the races conducted between the 
			 \textbf{swiftest} of the boats. 
			
		\newpage 
		\subsection{}
		\subsubsection{\textcolor{brickred}{condescend} (v)}
		2- do something in a haughty way, as though it is below one's dignity or level of importance. deign, stoop
		\textcolor{gold}{"we'll be waiting for twenty minutes before she condescends to appear"
		"Mark Twain's boat was so slow no other steamer would 
		condescend to race with it."
		"He had such disdain for us, he would not condescend to speak before
		our group."}
		
		\subsubsection{\textcolor{brickred}{candor} (n)}
		frankness,
		openness,
		honesty
		\textcolor{gold}{"a man of refreshing candor"
		"With the utmost candor, Twain 
		comments that..."
		"When we cannot speak with candor, we utilize euphemisms."}
		
		\subsubsection{\textcolor{brickred}{mortify} (v)}
		embarrass,
		humiliate,
		chagrin,
		shame
		\textcolor{gold}{"she was mortified to see her wrinkles in the mirror"
		"Nothing 
		would mortify Twain more than..."}
		
		\subsubsection{\textcolor{brickred}{jocose} (adj)}
		playful or humorous.
		\textcolor{gold}{"a jocose allusion"
		"Twain wrote in a jocose 
		manner about the races his steamer had."}
		
		\subsubsection{\textcolor{brickred}{\hl{malign}} (v)}
		speak about (someone) in a spitefully critical manner.
		defame,
		slander
		\textcolor{gold}{"don't you dare malign her in my presence"
		"With quiet humor he continued to malign the riverboat."
		"to malign a defeated adversary"}
		
		\newpage
		\subsection{}
		\subsubsection{\textcolor{brickred}{omnipotent} (adj)}
		almighty, unlimited in power and authority
		\textcolor{gold}{"God is described as omnipotent and benevolent"
		"The riverboat pilot was a man considered omnipotent by all."}
		
		\subsubsection{\textcolor{brickred}{zenith} (n)}
		\textbf{the time} at which...
		\textcolor{gold}{"under Justinian, the Byzantine Empire reached its zenith of influence"
		"Under the aegis of an adroit master, he reached the zenith of his career."}
		
		\subsubsection{\textcolor{brickred}{fledgling} (n)}
		(a young bird that has just fledged.) a person or organization that is immature, inexperienced, or underdeveloped.
		emerging,
		emergent,
		arising
		
		\textcolor{gold}{"A New York businessman accused of defrauding a fledgling Broadway production has been held without bail"
		"Starting out as a 
		fledgling pilot's apprentice, he could not \textbf{abjure} dreams of the 
		time he would become..."}
		
		\subsubsection{\textcolor{brickred}{peremptory} (adj) [pr·emp·tr·ee]}
		1- (especially of a person's manner or actions) insisting on immediate attention or obedience, especially in a brusquely imperious way.
		\textcolor{gold}{"“Just do it!” came the peremptory reply"}\\
		2- incontrovertible, not open to appeal or challenge; final.
		\textcolor{gold}{"there has been no disobedience of a peremptory order/command of the court"
		"No one had the temerity to disobey the officer's peremptory order."}
		
		\subsubsection{\textcolor{brickred}{precedent} (n)}
		an earlier event or action that is regarded as an example or guide to be considered in subsequent similar circumstances.
		model,
		exemplar,
		example
		\textcolor{gold}{"Any criticism of the pilot would 
		establish a pernicious precedent that would have }
		\textbf{undermined} (subvert,
		sabotage,
		threaten,
		weaken,
		diminish) \textcolor{gold} {the pilot's limitless authority."
		"there are substantial precedents for using interactive media in training"}
		\\
		\\
		- abjure:
		renounce,
		relinquish,
		reject,
		dispense with,
		forgo,
		"his refusal to abjure the Catholic faith"\\
		- unfettered: unrestrained'
		unrestricted,
		uninhibited
		"unfettered artistic genius"\\
		- hamper (v): hinder, impede, obstruct\\
		- monarch\\
		- quorum
		
		\newpage
		\subsection{}
		\subsubsection{\textcolor{brickred}{wheedle} (v) [wee·dl]}
		use flattery or coaxing in order to persuade someone to do something or give one something. 
		coax,
		cajole,
		persuade
		\textcolor{gold}{"she wheedled her way on to the guest list"
		"the gamblers 
		were trying to wheedle him into a card game."
		"He's just a piece of lowly scum who spends his time wheedling pensioners out of their savings over the phone."
		"I can't believe I let Seth wheedle }(or \textbf{swindle} here) \textcolor{gold}{ me out of my favorite pencil case!"}
		
		\subsubsection{\textcolor{brickred}{rustic} (adj)}
		relating to the countryside; rural, countrified.
		\textcolor{gold}{"His rustic appearance confirmed 
		that fact."
		"the unblemished charm of rustic life has been a } \textbf{perennial} (everlasting, perpetual) \textcolor{gold}{source of inspiration for the painter"}
		
		\subsubsection{\textcolor{brickred}{jubilant} (adj) [joo·buh·luhnt]}
		exultant,
		triumphant,
		joyful,
		rejoicing
		\textcolor{gold}{"When the first hand was dealt, a jubilant 
		expression came over his face."}
		
		\subsubsection{\textcolor{brickred}{decorum} (n) [de·kow·ruhm]}
		(\textbf{decorous}, \textbf{indecorous == unseemly} (adj)) politeness, decency, behavior in keeping with good taste and \underline{propriety} [pruh·prai·uh·tee].
		\textcolor{gold}{"you exhibit remarkable modesty and decorum"
		"Repress your \textbf{uncouth} manners and act with at the party. "
		"All 
		of the proper deconun was put aside."}
		
		\subsubsection{\textcolor{brickred}{charlatan} (n) [shaar·luh·tn]}
		a person falsely claiming to have a special knowledge or skill; a fraud/quack.
		\textcolor{gold}{"At this point the victim, the 
		charlatan. \textbf{removed the veneer of respectability}, and showed a 
		hand of four aces!"}
		\\
		\\
		a clandestine \textbf{confederate} (accomplice) of the "rich cattle farmer."\\
		"They had 
		been planning this duplicity for many weeks."
		"a businessman \textbf{swindled} investors out of millions of dollars"

\newpage		
\setcounter{section}{31}
\setcounter{subsection}{0}
%\section*{}

	\subsection{}
	\subsubsection{\textcolor{brickred}{heresy} (n) [heh·ruh·see]}
	opinion profoundly at odds with what is generally accepted.
	\textcolor{gold}{"the heresy of being uncommitted to the right political dogma"
	"It is not a heresy to our democratic beliefs to state that..."
	"political heresy"}
	
	\subsubsection{\textcolor{brickred}{prudent} (adj)}
	acting with or showing care and thought for the future. wise,
	judicious,
	sagacious,
	sage,
	shrewd,
	advisable,
	sensible,
	cautious,
	careful,
	canny.
	\textcolor{gold}{"The prudent person will choose between cogent  and }\textbf{specious} (ostensible, superficially plausible, but actually wrong. misleadingly attractive.) \textcolor{gold}{propaganda efforts."
	"no prudent money manager would authorize a loan without first knowing its purpose"}
	
	\subsubsection{\textcolor{brickred}{ostensible} (adj)}
	stated or appearing to be true, but not necessarily so.
	\textcolor{gold}{"the real dispute which lay behind the ostensible complaint"
	"propaganda has the ostensible purpose of  informing the public."}
	
	\subsubsection{\textcolor{brickred}{fervid} (adj)}
	intensely enthusiastic or passionate, especially to an excessive degree. ardent, vehement \textbf{fervid\textgreater fervent}
	\textcolor{gold}{"his fervid protestations of love"
	"the most fervid propagandists"}
	
	\subsubsection{\textcolor{brickred}{spurious} (adj)}
	not being what it purports to be; false or fake. bogus, specious,
	factitious,
	counterfeit,
	fraudulent.
	\textcolor{gold}{"separating authentic and spurious claims"
	"The ability to distinguish the spurious from the true facts requires more than a perfunctory examination"
	"In the conflagration that followed, no one questioned whether the original charge had been spurious"}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{propagate} (v)}
	spread and promote (an idea/theory/...) widely.
	\textcolor{gold}{"the French propagated the idea that the English were drunkards"
	"the  inherent right to propagate ideas and try  to  win converts."}
	
	\subsubsection{\textcolor{brickred}{anomaly} (n)}
	something that deviates from what is standard, normal, or expected. oddity,
	peculiarity,
	abnormality,
	irregularity
	\textcolor{gold}{"We do not look upon an idea different from ours as an anomaly that should be precluded."}
	
	\subsubsection{\textcolor{brickred}{innocuous} (adj)}
	($\ne$ unctuous) not harmful or offensive.
	\textcolor{gold}{"an innocuous question/belief" "There appears to be no such thing as an innocuous heresy"}
	
	\subsubsection{\textcolor{brickred}{surfeit} (n) [sur·fuht
		]}
	excess,
	surplus,
	abundance.
	
	\textcolor{gold}{"a surfeit of food and drink" "we  are  accosted by  a surfeit of  propaganda" "a respite from the surfeit of TV commercials"}
	
	\subsubsection{\textcolor{brickred}{milieu} (n) [meel·yoo
		]}
	(a person's social) environment, background,
	setting.
	\textcolor{gold}{"Gregory came from the same aristocratic milieu as Sidonius" "We live in a milieu of ubiquitous bombardment." "It is incongruous to find an abstemious person in a milieu of avarice and affluence."}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{strident} (adj)}
	(of a sound) loud and harsh; grating, shrill.
	
	\textcolor{gold}{"his voice had become increasingly strident" "As the quantity of propaganda becomes greater, ideas are presented in more strident tones."}
	
	\subsubsection{\textcolor{brickred}{concomitant} (adj)}
	naturally \underline{accompanying} or \underline{associated}.
	
	\textcolor{gold}{"she loved travel, with all its concomitant worries" "The concomitant situation that develops with the stepped-up propaganda is one in which the individual retreats into a state of \textbf{lassitude}."}
	
	\subsubsection{\textcolor{brickred}{lassitude} (n)}
	a state of physical or mental weariness; lack of energy. lethargy,
	listlessness,
	weariness,
	languor,
	sluggishness,
	enervation,
	apathy
	\textcolor{gold}{"she was overcome by lassitude and retired to bed"}
	
	\subsubsection{\textcolor{brickred}{deleterious} (adj)}
	detrimental,
	injurious,
	inimical,
	pernicious
	\textcolor{gold}{ "It has the deleterious result  of reducing its efficacy upon the individuals or groups who were its objective."}
	
	\subsubsection{\textcolor{brickred}{efficacy} (n)}
	effectiveness
	\textcolor{gold}{"there is little information on the efficacy of this treatment"}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{dissent} (v)}
	hold or express opinions that are at variance with those commonly or officially held. differ.
	
	\textcolor{gold}{"two members dissented from the majority" "Those who dissent from the..."}
	
	\subsubsection{\textcolor{brickred}{ferment} (n)}
	uproar, agitation, turmoil. agitation and excitement among a group of people, typically concerning major change and leading to trouble or violence.
	\textcolor{gold}{"a period of political and religious ferment" "Where there is no open ferment of ideas, the possibility of discerning the true from the spurious is \textbf{attenuated}."}
	(v: incite or stir up (trouble or disorder).
	"the politicians and warlords who are fermenting this chaos")
	
	\subsubsection{\textcolor{brickred}{attenuated} (adj)}
	weakened, thinned, decreased. having been reduced in force, effect, or value.
	\textcolor{gold}{"it appears likely that the courts will be given an attenuated role in the enforcement of these decisions" "The strength of her appeal was attenuated by the flamboyant embellishments for which many had a strong aversion."}
	(attenuate (v): reduce the force, effect, or value of.)
	
	\subsubsection{\textcolor{brickred}{arbiter} (n)}
	adjudicator,
	arbitrator,
	judge. a person who settles a dispute or has ultimate authority in a matter.
	\textcolor{gold}{"the Secretary of State is the final arbiter" "In a democracy, the  inevitable arbiter of what propaganda is to be permitted is the people."}
	
	\subsubsection{\textcolor{brickred}{incumbent} (adj)}
	obligatory/
	mandatory/
	necessary/
	compulsory for (someone) as a duty or responsibility.
	
	\textcolor{gold}{"the government realized that it was incumbent on them to act" "It is incumbent on us to be zealous in combating the deleterious effects of drugs." "t is incumbent upon each citizen to..."}
	2- (adj/n)(of an official or regime) currently holding office.
	"the incumbent President was defeated" "the present incumbent will soon be retiring"
	\\\\
	\textbf{detest} (v): dislike intensely. abhor, loathe, despise, abominate, execrate.\\ "she really did detest his mockery"
	
	\newpage
	\setcounter{section}{32}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{profound} (adj)}
	very great or intense.
	\textcolor{gold}{"As automation permeates many new areas of life, its effect upon us becomes \textbf{concomitantly} more profound. " "profound feelings of disquiet"}
	
	\subsubsection{\textcolor{brickred}{alleviate} (v)}
	ease, relive. make (suffering, deficiency, or a problem) less severe.
	\textcolor{gold}{"he couldn't prevent her pain, only alleviate it" "they alleviate the burden of..."}
	
	\subsubsection{\textcolor{brickred}{prodigious} (adj)}
	VA YOU FUCK. enormous, gargantuan.
	\textcolor{gold}{"the stove consumed a prodigious amount of fuel" "an accumulation of  information that is becoming more prodigious."}
	
	\subsubsection{\textcolor{brickred}{celerity} (n) [suh·leh·ruh·tee]}
	swiftness of movement. speed, rapidity, velocity.
	\textcolor{gold}{"He accepted the lucrative position with celerity."}
	
	\subsubsection{\textcolor{brickred}{expedite} (v)}
	speed up, accelerate, hasten, percipitate. make sth happen sooner or be accomplished more quickly.
	\textcolor{gold}{"he promised to expedite economic reforms" "help expedite the  selection of  pertinent information"}\\\\
	permeate [pur·mee·eit] = pervade\\
	"threatening to inundate our society."
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{usurp} (v)}
	take illegally or by force. seize, annex
	\textcolor{gold}{"Richard usurped the throne" "The instrument for the modern communicator is the cell phone, which has usurped the wire-connected stationary model."}
	
	\subsubsection{\textcolor{brickred}{paltry} (adj)}
	very small or meagre. petty, trivial, worthless
	\textcolor{gold}{"They exacerbated a paltry difference of opinion into a prodigious conflict." "she would earn a paltry £33 more a month" "naval glory struck him as paltry" "a paltry number of  minutes"}
	
	\subsubsection{\textcolor{brickred}{condone} (v)}
	accept (behaviour that is considered morally wrong or offensive).
	\textcolor{gold}{"Do you expect me to condone that reprehensible act with such celerity?" "the college cannot condone any behaviour that involves illicit drugs" "to condone the inconvenience caused by  the indiscriminate use of  this ubiquitous instrument."}
	
	\subsubsection{\textcolor{brickred}{trivial} (adj)}
	petty, of little value or importance.
	\textcolor{gold}{"huge fines were imposed for trivial offences" "carry on with significant or trivial conversations for seemingly endless time"}
	
	\subsubsection{\textcolor{brickred}{bizarre} (adj)}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{venerable} (adj)}
	respected,
	venerated,
	revered,
	reverenced.
	
	\subsubsection{\textcolor{brickred}{menial} (adj) [mee·nee·uhl]}
	not requiring much skill and lacking prestige. unskilled,
	lowly,
	humble,
	degrading
	\textcolor{gold}{"menial factory jobs" "the menial task of  mere conversation"}
	
	\subsubsection{\textcolor{brickred}{succinct} (adj)}
	briefly and clearly expressed. concise,
	brief,
	compact,
	condensed,
	laconic,
	terse.
	\textcolor{gold}{"succinct sentences"}
	
	\subsubsection{\textcolor{brickred}{ambiguous} (adj)}
	open to more than one interpretation. equivocal,
	ambivalent.
	\textcolor{gold}{"ambiguous phrases"}
	
	\subsubsection{\textcolor{brickred}{extraneous} (adj) [uhk·strei·nee·uhs]}
	1- irrelevant or unrelated to the subject being dealt with.
	2- external
	\textcolor{gold}{"one is obliged to wade through many pages of extraneous material" "when the transmitter pack is turned off no extraneous noise is heard"}\\\\
	- a single combined score is reported because it is more reliable than is a score for either task alone.\\
	- to convey meaning effectively.\\
	- others...; others...; and still others.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{archaic} (adj)}
	antiquated, antique.
	\textcolor{gold}{"prisons are run on archaic methods" "The flood  of  new  technology makes each  modern marvel appear archaic."}
	
	\subsubsection{\textcolor{brickred}{rabid} (adj)}
	having an extreme/fanatical support/belief in something.
	\textcolor{gold}{"the show's small but rabid fan base" "a rabid purchaser of the newest product" "a rabid political adherent."}
	
	\subsubsection{\textcolor{brickred}{emulate} (v)}
	imitate, mimic, match or surpass (a person or achievement), typically by imitation.
	\textcolor{gold}{"most rulers wished to emulate Alexander the Great" "to emulate friends"}
	
	\subsubsection{\textcolor{brickred}{\hl{facetious}} (adj) [fuh·see·shuhs]}
	treating serious issues with deliberately inappropriate humour; flippant. whimsical, glib, frivolous.
	\textcolor{gold}{"a facetious remark" "It would  not  be facetious to  claim  that scientists will persevere in  devising ways for us to contact each other by voice,  photographs, and  print messages that give us access to a more salubrious social network."}
	
	\subsubsection{\textcolor{brickred}{salubrious} (adj)}
	healthy
	healthful
	beneficial
	wholesome
	salutary
	\textcolor{gold}{"odours (odor) of far less salubrious origin"}\\\\
	
	fanatical (adj): 1- filled with excessive and single-minded zeal. extremist, zealous.
	"fanatical revolutionaries"
	2- obsessively concerned with something. enthusiastic,
	eager,
	fervent.
	"her husband was fanatical about tidiness"
	
	\newpage
	\setcounter{section}{33}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{\hl{complacent}} (adj)}
	smug,
	self-satisfied,
	pleased with oneself,
	proud of oneself,
	self-approving,
	self-congratulatory,
	self-admiring,
	self-regarding,
	gloating,
	proud.
	\textcolor{gold}{"you can't afford to be complacent about security" "With the paltry sum of five dollars in his pockets,  Robert Lacy was feeling far from complacent about the future."}
	
	\subsubsection{\textcolor{brickred}{somber} (adj)}
	1- dark or dull in colour or tone. "the night skies were sombre and starless"
	2- having or conveying a feeling of deep seriousness and sadness. gloomy, sad, solemn, stern.
	\textcolor{gold}{"he looked at her with a sombre expression" "it  was his somber estimate that no matter how frugal he was, his money would run out before the next day." "The deleterious results of his irate outburst put the previously jocose audience in a somber mood."}
	
	\subsubsection{\textcolor{brickred}{debilitate} (v)}
	hinder, delay, or \underline{weaken}. enfeeble,
	enervate,
	devitalize.
	\textcolor{gold}{"hard drugs destroy families and debilitate communities" "Hunger would debilitate him to the point where he could not continue his fervid search for Evelyn."}
	
	\subsubsection{\textcolor{brickred}{impetuous} (adj)}
	acting or done quickly and without thought or care. impulsive.
	\textcolor{gold}{"she might live to rue this impetuous decision" "There was no hope of an impetuous stranger suddenly thrusting money upon him."}
	
	\subsubsection{\textcolor{brickred}{occult} (n)}
	supernatural,
	magical,
	mystical.
	\textcolor{gold}{"an occult ceremony/power"}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{discreet} (adj)}
	($\ne$ \textbf{discrete} (adj): sep\textbf{\underline{a}}rate, distinct, individual)\\
	1- careful and prudent in one's speech or actions, especially in order to keep something confidential/avoid embarrassment. careful,
	circumspect,
	cautious,
	wary.
	2- unobtrusive,
	inconspicuous,
	subtle,
	low-key.\\
	\textcolor{gold}{"we made some discreet inquiries" "I knew I could \textbf{confide} ($\ne$ confine) in Caryl-Sue because she has a reputation for being discreet" "a discreet cough(2)/question(1)"}
	
	\subsubsection{\textcolor{brickred}{foment} (v)}
	\underline{instigate} or \underline{stir up} (an undesirable/violent sentiment/course of action). incite.
	\textcolor{gold}{"they accused him of fomenting political unrest" "There was no need to foment opposition at the very beginning."}
	
	\subsubsection{\textcolor{brickred}{glean} (v)}
	obtain (information) from various sources, often with difficulty.
	\textcolor{gold}{ "...and  all Robert had been able to \textbf{glean from} the cryptic replies was that..."}
	
	\subsubsection{\textcolor{brickred}{quarry} (n) [kwaw·ree]}
	a thing/person that is chased/sought.
	\textcolor{gold}{"the security police crossed the border in pursuit of their quarry" "in  this immense city his quarry could be hiding in one of dozens of such places."}
	
	\subsubsection{\textcolor{brickred}{\hl{slovenly}} (adj)}
	(especially of a person or action) careless; excessively casual. slapdash.
	\textcolor{gold}{"slovenly speech" "His search, while it had to be concluded with  celerity,  could not  be  carried out  in such slovenly fashion/manner."}\\\\
	confide (v): 1- trust (sb) enough to tell them of a secret/private matter. "he confided in friends that he and his wife planned to separate" 2- tell someone about a secret/private matter while trusting them not to repeat it to others.
	"he confided his fears to his mother" 
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{abjure} (v) [ab·joor]}
	solemnly \textbf{renounce} (a belief, cause, or claim). relinquish, abstain from.
	\textcolor{gold}{"MPs were urged to abjure their Jacobite allegiance (= loyalty [uh·lee·jns])" "Robert's first step was to abjure fruitless searching" "In vain, the entire family tried to importune him to abjure gambling."}
	
	\subsubsection{\textcolor{brickred}{reproach} (v)}
	express to (someone) one's disapproval of or disappointment in their actions. 
	rebuke,
	reprove,
	scold,
	chide,
	reprimand = reprehend,
	admonish,
	chastise,
	censure,
	castigate
	\textcolor{gold}{"I do not reproach you for your actions." also, (2) "his wife reproached him with cowardice"}
	
	\subsubsection{\textcolor{brickred}{penitent} (adj)}
	VA p. 193 (Penitence) - feeling or showing sorrow and regret for having done wrong; repentant, contrite.
	\textcolor{gold}{"a penitent expression/person/confession"}
	
	\subsubsection{\textcolor{brickred}{evanescent} (adj)}
	\textcolor{gold}{"the evanescent Arctic summer" "His evanescent concerns disappeared." "the vicissitudes of life are evanescent"}
	
	\subsubsection{\textcolor{brickred}{tantamount} (adj)}
	equivalent to; virtually the same as.
	\textcolor{gold}{"the resignations were \textbf{tantamount to} an admission of guilt" "it was tantamount to a challenge"}\\\\
	sanguine [sang·gwn] = optimistic
	"there was a letter for him, and with tremulous fingers he tore it open."
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{propensity} (n)}
	tendency,
	inclination, proclivity, penchant.
	\textcolor{gold}{"his propensity for violence" "she had a propensity for folk music"}
	
	\subsubsection{\textcolor{brickred}{wary} (adj) [weh·ree]}
	cautious,
	careful,
	circumspect,
	watchful, prudent.
	\textcolor{gold}{"dogs which have been mistreated often remain very wary of strangers" "He knew he had to be wary so that Evelyn might not see him first." "Even milk has now been added to the list of foods \textbf{of} which we must be wary"}
	
	\subsubsection{\textcolor{brickred}{allay} (v)}
	diminish or put at rest (fear, suspicion, or worry). relieve or alleviate (pain or hunger).
	\textcolor{gold}{"some stale figs partly allayed our hunger" "the report attempted to educate the public and allay fears" "He tried hard to allay the sudden fear that came over him that he might not locate her."}
	
	\subsubsection{\textcolor{brickred}{deter} (v)}
	\underline{discourage} (someone) from doing something by instilling doubt or fear of the consequences. put off, dishearten.
	\textcolor{gold}{"only a health problem would deter him from seeking re-election" "Nothing would deter her from succeeding."}
	
	\subsubsection{\textcolor{brickred}{connoisseur} (n)}
	an expert judge.
	\textcolor{gold}{"a connoisseur of music" "And so, although he was far from a connoisseur of the dance..."}
	
	\newpage
	\setcounter{section}{34}
	\setcounter{subsection}{0}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{site} (n)}
	area, location.
	\textcolor{gold}{"the proposed site of a hydroelectric dam" "The newly married couple selected the site for their new home with meticulous care." "Disgruntled, he quit the site of his \textbf{vigil}."}
	
	\subsubsection{\textcolor{brickred}{vigil} (n)}
	wakeful watching, a period of keeping awake during the time usually spent asleep, especially to keep watch or pray.
	\textcolor{gold}{"my birdwatching vigils lasted for hours" "The hunter maintained a discreet and wary vigil as he waited for the propitious moment to bag his quarry."}
	
	\subsubsection{\textcolor{brickred}{cumbersome} (adj)}
	1- large or heavy and therefore difficult to carry or use, unwieldy, burdensome.\\
	2- slow/\underline{complicated} and therefore \underline{inefficient}.\\
	\textcolor{gold}{"cumbersome diving suits" "organizations with cumbersome hierarchical structures" "It  was  a cumbersome way of going about the hunt, but it was all that he  could think of at the moment." "With \textbf{rancor} he faced the cumbersome job of transporting the voluminous records to his new office."}
	
	\subsubsection{\textcolor{brickred}{interrogate} (v)}
	\textcolor{gold}{"to interrogate sb" "He  would interrogate the desk  clerks, and  perhaps he  might uncover a  pertinent clue to Evelyn's whereabouts."}
	
	\subsubsection{\textcolor{brickred}{divulge}(v) [duh·vuhlj]}
	make known (private/sensitive information). disclose, reveal.
	\textcolor{gold}{"I do not want to divulge my plans at the moment" "Even under duress, he was adamant and would not divulge the secret. " "If he could only get someone to divulge her hiding place. \textbf{Perhaps tomorrow would culminate in success.}"}\\\\
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{fluctuate} (v)}
	rise and fall irregularly in number or amount. shift, alter, alternate.
	\textcolor{gold}{"trade with other countries tends to fluctuate from year to year" "He would fluctuate between high hopes of finding Evelyn and \textbf{unmitigated} despair when he was almost ready to desist in his  search."}
	
	\subsubsection{\textcolor{brickred}{unmitigated} (adj)}
	absolute; unqualified. as bad as can be.
	\textcolor{gold}{"the tour had been an unmitigated disaster" "an unmitigated liar." "What was once viewed as unmitigated brutality"}
	
	\subsubsection{\textcolor{brickred}{commodious} (adj)}
	roomy and comfortable. capacious,
	spacious, ample.
	\textcolor{gold}{"they moved to a more commodious dwelling" "Robert waited in the commodious lobby, replete with large, \textbf{antiquated} pieces of furniture."}
	
	\subsubsection{\textcolor{brickred}{antiquated} (adj)}
	old-fashioned or outdated.
	\textcolor{gold}{"this antiquated central heating system" "antiquated prejudice"}
	
	\subsubsection{\textcolor{brickred}{di\underline{shevel}ed} (adj)}
	(of a person's hair/clothes/appearance) untidy; disordered.//
	-dishevel (v): make (a person's hair/clothes) untidy.
	\textcolor{gold}{"One look at her wan face, slovenly dress, and disheveled hair was enough to inform Robert that he  needed no further \textbf{scrutiny}."}\\\\
	- mitigate (v): alleviate, attenuate, allay, make (sth bad) less severe, serious, or painful.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{tenacious} (adj)}
	1- tending to keep a firm hold of something; clinging or adhering closely.\\
	2- not readily relinquishing a position, principle, or course of action; determined. stubborn.
	\textcolor{gold}{"a tenacious grip" "this tenacious defence of local liberties" "He had been tenacious in following up every lead." "He held on to his antiquated beliefs with a tenacious obsession."}
	
	\subsubsection{\textcolor{brickred}{facade} (n)}
	a deceptive outward appearance. front.
	\textcolor{gold}{"her flawless public facade masked private despair" "The facade of hope he had worn for almost a week  was \textbf{crumbling}." "His face wore the most doleful facade"}
	
	\subsubsection{\textcolor{brickred}{asinine} (adj)}
	extremely stupid or foolish.
	\textcolor{gold}{"Lydia ignored his asinine remark" "Some of the questions seemed asinine."}
	
	\subsubsection{\textcolor{brickred}{grimace} (n)}
	an ugly, twisted expression on a person's face, typically expressing disgust, pain, or wry amusement.
	(grimace(v): make a grimace. "I sipped the coffee and grimaced")
	\textcolor{gold}{"she gave a grimace of pain" "he replied, with a grimace, "Fiancee."" "She could not abjure a grimace when she saw the disheveled figure"}
	
	\subsubsection{\textcolor{brickred}{calumny} (n)}
	the making of false and defamatory statements about someone in order to damage their reputation; slander.
	\textcolor{gold}{"a bitter struggle marked by calumny and litigation" "He was incredulous and accused the police of calumny against her good name and reputation." "The woman was noted for her vituperative calumny against her innocuous neighbor."}\\\\
	"where the "punk" coterie \textbf{congregated}"
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{pittance} (n)}
	a very small/inadequate amount of money. PAPASI. VA p.93
	\textcolor{gold}{"he paid his workers a pittance" "Despite his abstemious and parsimonious way of  living,  his  money had been reduced to a  mere pittance."}
	
	\subsubsection{\textcolor{brickred}{au courant} (adj)}
	aware of what is going on; well informed, up to date, acquainted.
	\textcolor{gold}{"they were \textbf{au courant with} the literary scene" "He  had never been au courant with the hippies and punks."}
	
	\subsubsection{\textcolor{brickred}{fastidious} (adj)}
	VA p.163. very attentive to and concerned about accuracy and detail. scrupulous, meticulous, assiduous, choosy.
	\textcolor{gold}{"she dressed with fastidious care" "He was always fastidious about proper dress and behavior." "He was so fastidious about table manners that he lost his equanimity when his son reached for the bread."}
	
	\subsubsection{\textcolor{brickred}{noisome} (adj)}
	very disagreeable or unpleasant. (having an extremely offensive smell.)
	\textcolor{gold}{"a noisome concoction of which cheap port is the basis" "surrounded by a coterie of  the most noisome individuals he had ever seen." "It was inevitable that they discover the hidden body by its noisome aroma."}
	
	\subsubsection{\textcolor{brickred}{unkempt} (adj)}
	(especially of a person) having an untidy or \underline{disheveled} appearance. (kempt)
	\textcolor{gold}{"Evelyn was not incongruous, for she herself was unkempt."}\\\\
	- "uncouth (couth) manners made him recoil in unmitigated disgust."\\
	- old hand (n): a person with a lot of experience in something. expert.
	"to be an old hand at sth"\\
	- "The words you learn are valuable, the method is equally so."\\
	- "And now that seemingly male spectacle is attracting women."
	
	\newpage
	\setcounter{section}{35}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{parable} (n) [peh·ruh·bl]}
	a moral story (told by Jesus in the Gospels), allegory, fable, lesson.
	\textcolor{gold}{"the parable of the blind men and the elephant"}
	
	\subsubsection{\textcolor{brickred}{whimsical} (adj)}
	1- \underline{playful}ly \underline{quaint} or \underline{fanciful}, especially in an appealing and amusing way. mischievous, humorous, witty.\\
	2- volatile, capricious, mercurial.\\
	\textcolor{gold}{"a whimsical sense of humor" "This story form is far from antiquated as shown by the whimsical approach to life taken by the modern Aesop. James Thurber."}
	
	\subsubsection{\textcolor{brickred}{lampoon} (v)}
	satirize,
	mock,
	ridicule,
	make fun of,
	poke fun at,
	caricature.\\
	(\textbf{lampoon} (noun) =$>$ a speech or text lampooning someone or something.)
	\textcolor{gold}{"His stories lampoon the strange behavior of his fellow men."}
	
	\subsubsection{\textcolor{brickred}{countenance} (v)}
	admit as acceptable or possible. tolerate, approve of.
	(noun =$>$ a person's face or facial expression. "his impenetrable eyes and inscrutable countenance give little away")
	\textcolor{gold}{"If we want to live in a salubrious milieu, we can not countenance the noisome fumes that are deleterious to health." "he was reluctant to countenance the use of force" "Thurber seems unable to countenance the ideas that permeate our society regarding the rules by which we should live."}
	
	\subsubsection{\textcolor{brickred}{sanctimonious} (adj)}
	making a show of being morally superior to other people.self-righteous,
	holier-than-thou,
	churchy, pious.
	\textcolor{gold}{"what happened to all the sanctimonious talk about putting his family first?" "We should eschew our sanctimonious facade"}\\\\
	\textbf{fabulist}, \textbf{fable}\\
	notion: 1- idea 2- impulse "children have different notions about the roles of their parents" "she had a notion to call her friend at work"
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{equanimity} (n)}
	mental calmness, composure, and evenness of temper, self-control.
	\textcolor{gold}{"she accepted both the good and the bad with equanimity" "With equanimity he hunted for a hare and soon found one." "These turbulent times require a leader who does not go into a capricious pique, but rather one who faces acrimonious criticism with equanimity."}
	
	\subsubsection{\textcolor{brickred}{effrontery} (n)}
	insolent or (=) impertinent (= showing a rude and arrogant lack of respect. rude.) behavior. audacity,
	temerity,
	boldness.
	\textcolor{gold}{"one juror had the effrontery to challenge the coroner's decision" "Do you have the effrontery to take that supercilious and facetious attitude toward something as sinister as this?"}
	
	\subsubsection{\textcolor{brickred}{nonentity} (n)}
	a person/thing with no special/interesting qualities; \underline{an unimportant person}/thing.
	\textcolor{gold}{"a political nonentity" ""You are a nonentity," he scoffed at the tortoise." "He was a precocious youngster, but he soon reached the nadir of his career, lost all of his prestige, and became a nonentity"}
	
	\subsubsection{\textcolor{brickred}{flabbergasted} (adj)}
	greatly surprised or astonished. astounded.
	flabbergast (v)\\
	\textcolor{gold}{"this news has left me totally flabbergasted" "When the hare crossed the finish line, the flabbergasted tortoise had gone approximately eight and three-quarter inches." "When the judge exonerated the charlatan, we were all flabbergasted"}
	
	\subsubsection{\textcolor{brickred}{debacle} (n)}
	a sudden and ignominious failure; a fiasco.
	\textcolor{gold}{"the economic debacle that became known as the Great Depression"}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{vivacious} (adj) [vuh·vei·shuhs]}
	attractively lively and animated (typically used of a woman).
	\textcolor{gold}{"her vivacious and elegant mother" "With alacrity, this vivacious youngster told the wolf the address to which she was going." "They were struck by the anomaly of one twin who was phlegmatic while the other
		was vivacious"}
	
	\subsubsection{\textcolor{brickred}{gaunt} (adj)}
	lean and \underline{haggard} (VA p.54), especially because of suffering/hunger/age.
	\textcolor{gold}{"Hungry and gaunt, the wolf rushed to the house." "Women strive for the slender and au courant gaunt look."}
	
	\subsubsection{\textcolor{brickred}{mien} (n) [meen]}
	appearance, bearing. a person's look or manner, especially one of a particular kind indicating their character or mood.
	\textcolor{gold}{"he has a cautious, academic mien" "While the figure was 
		dressed like her grandmother, the little girl surmised with 
		only a perfunctory glance that it didn't have the old lady's 
		mien." "She had a mien of humility, but it was only a facade."}
	
	\subsubsection{\textcolor{brickred}{hirsute} (adj) [hur·soot]}
	hairy
	\textcolor{gold}{"their hirsute chests" "She approached and became cognizant of the hirsute 
		face of the wolf." "You may have discerned that it is no longer the latest vogue among boys to permit
		their faces to become hirsute"}
	
	\subsubsection{\textcolor{brickred}{refute} (v)}
	prove to be wrong or false; \underline{disprove}.
	\textcolor{gold}{"these claims have not been convincingly refuted" "Thurber arrives at a moral for this story 
		that anyone would find difficult to refute" "He did not waste time trying to refute an irrelevant and \textbf{tortuous 
		argument}."}\\\\
	- \textbf{quench} (v): satisfy (one's thirst) by drinking. satisfy (a desire). "he only pursued her to quench an aching need" 2- extinguish (a fire). "firemen hauled on hoses in a desperate bid to quench the flames" 3- stifle or suppress (a feeling). "fury rose in him, but he quenched it"\\
- "through enjoyment and \textbf{perusal} (scrutiny, study, examination, inspection, motale e) of nature."
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{pensive} (adj)}
	engaged in, involving, or reflecting deep or serious thought. VA p.156
	\textcolor{gold}{"a pensive mood" "Thurber's stories are written in a jocose manner, but they 
		contain enough serious matter to make one pensive."}
	
	\subsubsection{\textcolor{brickred}{whet} (v) [wet]}
	\underline{excite}/\underline{stimulate} (someone's desire/interest/appetite).
	\textcolor{gold}{"here's an extract to whet your appetite" "This challenge served to whet their interest, arid they agreed 
		with gusto." "You cannot whet his desire for the theater with dubious histrionics." ""Star Trek" and its 
		successors continue to whet our appetite and bring excitement to our 
		screens."}
	
	\subsubsection{\textcolor{brickred}{stupor} (n)}
	daze, a state of near-unconsciousness or insensibility.
	\textcolor{gold}{"a drunken stupor" "The birds struck the glass; they were knocked into a stupor." "He was in such a stupor as a result of the accident that this precluded his 
		hearing my condolence."}
	
	\subsubsection{\textcolor{brickred}{\hl{wince}} (v)}
	flinch, give a slight involuntary grimace/shrinking movement of the body out of/in anticipation of pain or distress.
	\textcolor{gold}{"he winced at the disgust in her voice" "This caused the astute swallow to wince with pain." ". The hostile rebuke made the usually phlegmatic boy wince"}
	
	\subsubsection{\textcolor{brickred}{cliche} (n)}
	platitude,
	hackneyed/trite phrase,
	banality.
	\textcolor{gold}{ "the antithesis of the cliche we all accept."}\\\\
	"the stars of the original series are 
	\textbf{mobbed} when they make personal appearances."\\
	As long as space remains an almost total mystery, the unexplained 
	will capture our imaginations. 
	
	\newpage
	\setcounter{section}{36}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{genre} (n) [zhaan·ruh]}
	
	\textcolor{gold}{"One of the \textbf{foremost} (adj) in this genre was 
		Charlotte Bronte."}
	
	\subsubsection{\textcolor{brickred}{candid} (adj)}
	truthful and straightforward; frank. open.
	\textcolor{gold}{"she presented a candid 
		portrait of a woman caught up in a clandestine affair with 
		a married man."}
	
	\subsubsection{\textcolor{brickred}{unsavory} (adj)}
	disagreeable to taste, smell, or look at. also disagreeable and unpleasant because morally \underline{disreputable}.
	\textcolor{gold}{"It is reprehensible, but it doesn't require much gossip to give a person an unsavory reputation" "She took this unsavory subject and presented it 
		in a way that did not \textbf{degrade} the relationship."}
	
	\subsubsection{\textcolor{brickred}{degrade} (v)}
	treat/regard (sb) with contempt/disrespect. lower.
	\textcolor{gold}{"she thought that many supposedly erotic pictures degraded women" "Harry held the fallacious belief that the menial job would degrade him 
		in the eyes of his friends."}
	
	\subsubsection{\textcolor{brickred}{venial} (adj) [vee·nee·uhl]}
	slight/pardonable/forgivable/excusable sin/wrongdoing/fault/offense
	\textcolor{gold}{"we cannot prevent ourselves sometimes from dreaming of performing venial if not \textbf{mortal sins}" "The affair was 
		considered merely a venial sin because Jane was never false 
		in her feelings or her actions." "Betty's childish fabrications were judged venial sins, although they 
		mortified her mother."}\\\\
	- decrepit (adj)\\
	- The nineteenth century saw the woman novelist attain the 
	same prestige as men. England was prolific in producing 
	women writers.\\
	- Miss Bronte did not 
	disparage Jane's feelings or besmirch her character.\\
	- When he heard through the grapevine that the fat was in the fire, 
	he knew he had to keep a stiff upper lip so as not to spill the beans.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{epitome} (n) [uh·pi·tuh·mee]}
	a person/thing that is a perfect example of a particular quality/type. 
	personification,
	embodiment,
	incarnation,
	paragon.
	\textcolor{gold}{"she looked the epitome of elegance and good taste" "The epitome of French romantic writers in the nineteenth 
		century was Victor Hugo." "The Taj Mahal in India is said to be the epitome of grace as an edifice."}
	
	\subsubsection{\textcolor{brickred}{dexterity} (n)}
	skill in performing tasks, especially with the hands. 
	deftness,
	adeptness,
	adroitness.
	\textcolor{gold}{"her dexterity with chopsticks" "With the utmost dexterity he wrote 
		poetry, novels, and drama." "With dexterity he thwarted the pugnacious and belligerent adversary."}
	
	\subsubsection{\textcolor{brickred}{grotesque} (adj)}
	comically/repulsively ugly or \underline{distorted}.
	malformed,
	deformed,
	misshapen,
	misproportioned. also, incongruous/inappropriate to a shocking degree. 
	outrageous,
	monstrous,
	astonishing,
	preposterous.
	
	\textcolor{gold}{"a lifestyle of grotesque luxury" "grotesque facial distortions" "His highly popular novels, are replete with melodramatic situations and grotesque characters."}
	
	\subsubsection{\textcolor{brickred}{compassion} (n)}
	\underline{sympath}etic \underline{pity} and concern for the sufferings or misfortunes of others. empathy.
	\textcolor{gold}{"We all felt deep compassion for the innocent progeny, who were bereft of their 
		parents who had succumbed during the conflagration." "the victims should be treated with compassion" "He had a 
		profound sense of social justice and a compassion for the poor, 
		\textbf{hap}less, and \textbf{downtrodden}."}
	
	\subsubsection{\textcolor{brickred}{repugnant} (adj)}
	extremely distasteful; unacceptable. 
	abhorrent,
	revolting,
	repulsive,
	repellent.
	\textcolor{gold}{"The sight of the corpse was repugnant to the squeamish \textbf{onlookers}." "the thought of going back into the fog was repugnant to him" "When the repugnant 
		rule came to an end, the expatriate returned. He was received 
		with \textbf{adulation} and acclaim as the idol of the Third Republic. "}\\\\
	- downtrodden (adj): \underline{oppressed}/treated badly by people in power. 
	subjugated, persecuted, subdued.
 	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{acme} (n)}
	peak,
	pinnacle,
	zenith,
	summit.
	\textcolor{gold}{"At the acme of his power, the dictator was obsessed with the belief that 
		those who dissented were trying to usurp his position." "physics is the acme of scientific knowledge" "The movement toward realism in the English novel of the 
		nineteenth century reached its acme with the works of 
		Charles Dickens and William Thackeray."}
	
	\subsubsection{\textcolor{brickred}{copious} (adj)}
	VA p.165. 
	abundant,
	superabundant,
	plentiful,
	ample,
	\textbf{profuse}.
	\textcolor{gold}{"She lost her decorum and wept copious tears at the poignant story." "she took copious notes" "Among his copious works are 
		Oliver Twist, a candid exposure of the repugnant poor laws."}
	
	\subsubsection{\textcolor{brickred}{vehemently} (adv) [vee·uh·muhnt·lee]}
	in a forceful, passionate, or intense manner; with great feeling.
	\textcolor{gold}{"He objected vehemently to a vote taking place in the absence of a \textbf{quorum}." "he vehemently denied any suggestion of improper conduct" "sth is vehemently attacked"}
	
	\subsubsection{\textcolor{brickred}{depict} (v)}
	show or represent by a drawing, painting, or other art form. represent,
	picture,
	illustrate. also, portray in words; describe.
	\textcolor{gold}{"As a \textbf{perspicacious} (=perceptive) newspaper reporter, he felt it \textbf{incumbent} (obligatory,
		mandatory, compulsory, binding) upon him to
		depict the \textbf{abortive} (failing to produce the intended result.) \textbf{coup} as a reprehensible act." "paintings depicting Old Testament scenes" "youth is depicted as a time of vitality and good health" "... in which the 
		author wanted to depict the infamous life in a factory during 
		an early period of the industrial revolution"}
	
	\subsubsection{\textcolor{brickred}{naive} (adj)}
	showing a lack of experience/wisdom/judgment.
	innocent,
	unsophisticated,
	artless,
	ingenuous,
	inexperienced.
	\textcolor{gold}{"The urbane gentleman was flabbergasted by the fervid interest in wrestling shown
		by the naive young girl." "the rather naive young gentleman had been totally misled" "Andy had a sweet, naive look when he smiled"}\\\\
	- The novels, aimed at exposing the \textbf{sordid} 
	and \textbf{pernicious} elements of English life, were said to have 
	helped \textbf{galvanize} people into action leading to improvement 
	in these conditions. 
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{perfidious} (adj) [pr·fi·dee·uhs]}
	deceitful and untrustworthy. treach\underline{e}rous
	\textcolor{gold}{"a perfidious lover" "She is a perfidious woman who has an insatiable desire to get 
		ahead in the world."}
	
	\subsubsection{\textcolor{brickred}{covet} (v) [kuh·vuht]}
	($\ne$ covert) (covetous) yearn to possess or have (something). desire, crave
	\textcolor{gold}{ "She covets the wealth of one man, but 
		when marriage is not \textbf{feasible} she succeeds in a plan to 
		\textbf{ingratiate} herself into the heart of her employer's son. "}
	
	\subsubsection{\textcolor{brickred}{ingratiate} (v)}
	(Ingratiating VA p.98)bring oneself into favor with someone by flattering or trying to please them. pache khaari kardan basically.
	\textcolor{gold}{"a social climber who had tried to ingratiate herself with the city \textbf{gentry}"}
	
	\subsubsection{\textcolor{brickred}{penury} (n) [peh·nyr·ee]}
	extreme poverty; \underline{destitution} (destitute (adj): VA p.113).
	\textcolor{gold}{"he died in a state of virtual(almost) penury" "The affair culminates in a debacle. She is exposed, her 
		husband leaves her, and she must live in penury in Europe."}
	
	\subsubsection{\textcolor{brickred}{ignominious} (adj)}
	humiliating,
	undignified,
	embarrassing,
	mortifying,
	shameful,
	disgraceful, deserving or causing public disgrace or shame.
	\textcolor{gold}{"This is the ignominious end for a clever, but misguided woman." "There was bedlam as the favored team went down to \textbf{ignominious defeat}
		at the hands of the underdog."}\\\\
	Their 
	marriage is not a salubrious one and Becky, who lives 
	ostentatiously, forms a surreptitious \textbf{liaison} [lee·ei·zaan] with another 
	man.\\\\
	- Along with the celebrations and historical 
	\textbf{reenactment}s, there was controversy regarding the lives of those who had 
	been here for many centuries before that \textbf{fateful} event.\\
	- It was to remove the ignominious portrayal of the Native American as savage 
	and wild that historians adopted 1992 as the year to \textbf{depict them in 
	their true light} as members of civilizations worthy of study and respect.
	
	\newpage
	\setcounter{section}{37}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{confront} (v)}
	
	\textcolor{gold}{"he confronted the robbers as they were trying to leave" "post-czarist Russia was \textbf{confronted with} a Ukrainian national movement" "usually the best thing you can do in an embarrassing situation is to confront it head on" "Tricia \textbf{confronted him with} her suspicions" "He attempted to confront the problem and solve 
		the enigma of how one might earn a living and yet not 
		become an ignominious slave to the task." "Why do we refuse to confront the unsavory problems of our times in a 
		candid and incisive way?"}
	
	\subsubsection{\textcolor{brickred}{antipathy} (n)}
	aversion,
	hostility,
	antagonism,
	animosity,
	enmity, dislike, distaste, hate.
	\textcolor{gold}{"his fundamental \textbf{antipathy to} capitalism" "He viewed the 
		industrial revolution with antipathy." "Her antipathy towards men was based on rather nebulous events that she 
		construed to prove that they were all perfidious."}
	
	\subsubsection{\textcolor{brickred}{servile} (adj) [sur·vl]}
	obsequious,
	sycophantic,
	subservient,
	fawning,
	toadying,
	ingratiating,
	unctuous, slavish.
	\textcolor{gold}{"he bowed his head in a servile manner" "the servile (slavish) condition of the peasants" "Man in a servile role to 
		extraneous possessions was a main target of his writings." "He found his servile position a degrading one and could not accept it
		with equanimity."}
	
	\subsubsection{\textcolor{brickred}{volition} (n)}
	\textcolor{gold}{"without conscious volition she backed into her office" "By his own volition he gave up friends and 
		\textbf{comforts} for a two year \textbf{sojourn} by himself at Walden Pond." "they choose to leave early \textbf{of their own volition}" "He was a tenacious competitor, and at his own volition he placed his title 
		in jeopardy on many occasions."}
	
	\subsubsection{\textcolor{brickred}{sojourn} (n/v) [sow·jrn]}
	\underline{a temporary stay.} \underline{stay somewhere temporarily.}
	\textcolor{gold}{"her 14 day sojourn in Rome" "she had sojourned once in Egypt" "The expatriate decided to make his sojourn in France a permanent one in 
		order to give up his nomadic way of life."}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{austere} (adj)}
	VA p.100.
	\textcolor{gold}{"an austere man, with a rigidly puritanical outlook" "conditions in the prison could hardly be more austere" "Thoreau's book about the austere but happy life at Walden Pond \textbf{propagated} his fame around the world." "the cathedral is impressive in its austere (\underline{unadorned}) simplicity" "her manner austere of dress"}
	
	\subsubsection{\textcolor{brickred}{\hl{felicitous}} (adj) [fuh·li·suh·tuhs]}
	apt, well put, \underline{well chosen} or suited to the circumstances.\\
	also, pleasing and fortunate.
	\textcolor{gold}{"a felicitous phrase/occa\textbf{s}ion" "the view was the room's only felicitous feature" "He found 
		it to be a felicitous experience." "This \textbf{nascent} business became 
		popular as women found ostrich feathers a felicitous addition to their 
		wardrobes."}
	
	\subsubsection{\textcolor{brickred}{halcyon} (adj) [hal·see·uhn]}
	denoting a period of time in the past that was \underline{idyllic}ally happy and \underline{peaceful}. 
	serene,
	calm, tranquil.
	
	\textcolor{gold}{"the halcyon days of the mid-1980s, when profits were \textbf{soaring}" "At the end of the experiment he recalled the halcyon days with pleasure." "During the turbulent days of the war, they wished for the halcyon days of earlier times. "}
	
	\subsubsection{\textcolor{brickred}{tenable} (adj)}
	VA p.260.
	defensible,
	justifiable,
	defendable,
	supportable,
	sustainable.
	\textcolor{gold}{"such a simplistic approach is no longer tenable" "The only tenable way of life is one in 
		harmony with nature; material possessions are \textbf{superfluous}." "When he found his sinecure was no longer tenable, he felt it a propitious time to resign."}
	
	\subsubsection{\textcolor{brickred}{\hl{superfluous}} (adj)}
	($\ne$ \textbf{superficial}) unnecessary, especially through being more than enough. surplus, excess.
	\textcolor{gold}{"the purchaser should avoid asking for superfluous information" "Because he was an itinerant worker, he had to disdain carrying superfluous equipment."}\\\\
	- In this idyllic setting he was able to...
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{motivate} (v)}
	 inspire, stimulate, provoke.
	\textcolor{gold}{"He taught that man has a 
		subconscious mind in which he keeps \textbf{repugnant} memories 
		that come to the surface \textbf{surreptitiously} and motivate 
		behavior." "he was primarily motivated by the desire for profit"}
	
	\subsubsection{\textcolor{brickred}{rationalize} (v)}
	justify
	\textcolor{gold}{"she couldn't rationalize her urge to return to the cottage" "Man often tries to rationalize his actions, when, in 
		reality, they are really the result of suppressed memories 
		coming to the surface." "It is pathetic the way some citizens rationalize their apathy during election 
		years."}
	
	\subsubsection{\textcolor{brickred}{therapy} (n)}
	\underline{treatment} intended to relieve/heal a disorder.
	\textcolor{gold}{"a course of antibiotic therapy" "Freud's approach to the disturbed 
		person was to attempt therapy by examining the dreams."}
	
	\subsubsection{\textcolor{brickred}{nascent} (adj) [nei·snt]}
	VA p.316, incipient,
	fledgling [flej·luhng]
	\textcolor{gold}{"His beard was in its nascent state; it would soon be a hirsute masterpiece." "the nascent space industry" "Only 
		with the \textbf{airing} (\underline{express} publicly.) of deleterious, buried emotions can the person 
		move from the nascent stage to that of full health. "}
	
	\subsubsection{\textcolor{brickred}{iconoclast} (n)}
	VA. p.277, 
	critic,
	skeptic,
	heretic,
	nonconformist,
	dissident, a person who attacks cherished beliefs or institutions.
	\textcolor{gold}{"The iconoclast was in favor of \textbf{jettisoning} one of the traditions that had become 
		an intrinsic part of his life." "Freud was 
		considered an iconoclast in the field of psychology when his 
		ideas first appeared at the beginning of the twentieth century."}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{erudite} (adj) [eh·ruh·dait]}
	learn\textbf{e}d,
	scholarly, \textbf{lettered},
	cultivated.
	\textcolor{gold}{"Ken could turn any conversation into an erudite discussion" "Despite their dubious (suspect) 
		education and training in this field, they discuss symptoms 
		and cures on a most erudite fashion."}
	
	\subsubsection{\textcolor{brickred}{phobia} (n)}
	an extreme/irrational/abnormal fear of or aversion to something.
	\textcolor{gold}{"he had a phobia about being under water" "Should a person 
		express a fear of heights, this phobia is examined; events 
		from childhood are considered \textbf{germane} to the problem." "She could not countenance the sight of a lethal weapon; it was tantamount to
		a phobia with her."}
	
	\subsubsection{\textcolor{brickred}{germane} (adj)}
	relevant,
	pertinent,
	applicable,
	apposite,
	\textbf{apropos}.
	\textcolor{gold}{"that is not germane to our theme" ""}
	
	\subsubsection{\textcolor{brickred}{vertigo} (n)}
	\underline{dizziness}, a sensation of \underline{whirling} and loss of balance, associated particularly with looking down from a great height, or caused by disease affecting the inner ear or the vestibular nerve; \underline{giddiness}.
	\textcolor{gold}{"... an onset of would surely follow." "to explain the feelings of 
		vertigo that accompany height."}
	
	\subsubsection{\textcolor{brickred}{\hl{conducive}} (adj) [kuhn·doo·suhv]}
	\underline{helpful} to,
	useful for,
	favorable,
	beneficial,
	valuable,
	advantageous,
	opportune,
	propitious.
	\textcolor{gold}{"The bedlam in the study hall was conducive not to good work habits." "the harsh lights and cameras were hardly \textbf{conducive to} a relaxed atmosphere" "For some reason, non-trained 
		people find the Freudian approach to the workings of the 
		human mind most \textbf{conducive to} their practicing as amateur 
		psychologists."}\\\\
	- whirl (v) [wurl]: move or cause to move rapidly around and around.
	
	\newpage
	\setcounter{section}{38}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{glib} (adj)}
	VA p.93. (of words or the person speaking them) fluent and voluble but insincere and shallow.
	\textcolor{gold}{"The charlatan  was able to \textbf{wheedle} money out of the naive audience with a glib talk on the medicine that would expunge pain." "she was careful not to let the answer sound too glib" "The teenagers, who are so glib when they speak of 
		"individuality", are turned into a \textbf{homogeneous} mass by the 
		latest craze in fashion."}
	
	\subsubsection{\textcolor{brickred}{homogeneous/homogenous} (adj) [how·mow·jee·nee·uhs/huh·maa·juh·nuhs]}
	of the same kind; alike.
	similar. consisting of parts all of the same kind. uniform.
	\textcolor{gold}{
		"timbermen prefer to deal with homogeneous woods" "culturally speaking the farmers constitute an extremely homogeneous group" ""}
	
	\subsubsection{\textcolor{brickred}{malleable} (adj)}
	(of some material such as metal) capable of being shaped or formed. hence, easily influenced; \underline{pliable}, \underline{amenable}.
	\textcolor{gold}{"they are as malleable and easily led as sheep" "How can youngsters who vehemently resist advice from the older generation become so malleable in the hands of those  who  "set" vogues?" "He ingratiated himself into their confidence, and the malleable crowd was shaped into a subjugated mass."}
	
	\subsubsection{\textcolor{brickred}{leger\underline{de}main} (n)}
	VA page 243. deception; trickery.
	\textcolor{gold}{"a classic piece of management legerdemain" "Or is there some group who, through legerdemain, switches styles and customs on us right before our eyes?"}
	
	\subsubsection{\textcolor{brickred}{trend} (n)}
	\textcolor{gold}{"an upward trend in sales and profit margins" "They could not follow the trend of his ideas, but his verbal dexterity galvanized the gullible listeners." "Today's teenagers seem to be quite gullible when it comes to embracing the latest trend in fashions."}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{stagnant} (adj)}
	1- (of water)\\
	2- showing no activity; dull and sluggish. inactive, motionless.
	\textcolor{gold}{"The fashion industry is cognizant of the fact that fashions must change rapidly and often or their economy would become stagnant" "The iconoclast has the propensity for reproaching those who feel complacent with leading a stagnant existence."}
	
	\subsubsection{\textcolor{brickred}{fatal} (adj)}
	(not just about death, it can mean "leading to failure or disaster.")
	\textcolor{gold}{"To the \textbf{consternation} of the \textbf{distraught parents} they learned their son was accused of using a lethal weapon on that fatal occasion." "there were three fatal flaws in the strategy" "It would prove fatal if this industry \textbf{were} not vigilant and prepared well in advance for a new fashion trend."}
	
	\subsubsection{\textcolor{brickred}{passé} (adj)}
	no longer fashionable; \underline{out of date}. outdated, archaic,
	obsolescent,
	obsolete,
	ancient,
	antiquated,
	superannuated.
	\textcolor{gold}{"As the old  fashion becomes passé and a new fashion seems to be in the making, the garment manufacturers cannot afford to \textbf{procrastinate}." "minis are passé—the best skirts are knee-length"}
	
	\subsubsection{\textcolor{brickred}{procrastinate} (v)}
	\underline{delay}/\underline{postpone action}; put off doing something.
	\textcolor{gold}{"the temptation will be to procrastinate until the power struggle plays itself out" "We all tend to procrastinate when faced with an \textbf{unsavory} task."}
	
	\subsubsection{\textcolor{brickred}{facet} (n)}
	1- one side of something many-sided, especially of a cut gem.\\
	2- a particular \underline{aspect}/feature of something.
	\textcolor{gold}{"Through every facet of publicity and advertising the industry exploits the natural desire for people to be au courant with the latest fashions." "a philosophy that extends to all facets of the business" "Edna recalled with nostalgia many facets of her school days."}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{foist} (v)}
	\underline{impose} an unwelcome/unnecessary person/thing on.
	\textcolor{gold}{"she had no desire to have an elderly relative foisted on her" "Once the fashion industry has been able to foist a new style on the teenager, the older generation tends to \textbf{stigmatize} it as some form of rebellion."}
	
	\subsubsection{\textcolor{brickred}{stigmatize} (v)}
	mark with stigmata (a disgrace). describe/regard as worthy of disgrace/great disapproval.
	\textcolor{gold}{"sth was stigmatized as sth"}
	
	\subsubsection{\textcolor{brickred}{capitulate} (v)}
	VA p.330. cease to resist an opponent/unwelcome demand; yield. surrender.
	\textcolor{gold}{"the patriots had to capitulate to the enemy forces" "What is often ignored is that the young consumers capitulate to what is originated by someone outside of their group."}
	
	\subsubsection{\textcolor{brickred}{audacity} (n)}
	a willingness to take bold risks. boldness,
	daring,
	intrepidity.
	\textcolor{gold}{"The feelings of individuality and audacity that the teenager gets from a  new style of dress result from the propensity of their elders to disparage them." "he whistled at the sheer audacity of the plan"}
	
	\subsubsection{\textcolor{brickred}{tantalize} (v)}
	\underline{torment} or \underline{tease} (sb) with the sight/promise of something that is unobtainable. (something good, but not deliver.) - excite the senses or desires of (someone).
	\textcolor{gold}{"such ambitious questions have long tantalized the world's best thinkers" "The clothing industry is busy planning how to tantalize the teenager with next year's "fashion.""}\\\\
	This \textbf{arbitrary} decision is guaranteed to \textbf{\hl{foment}} \textbf{consternation} among adults once again in the following year.\\
	- a profit-driven economy.\\
	- \textbf{scarce} $\approx$ sparse. (scarcity)\\
	- go-between (n) = an intermediary or negotiator. middleman.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{retort} (v)}
	say something in answer to a remark, typically in a sharp, angry, or witty manner. answer,
	reply,
	respond.
	\textcolor{gold}{"‘No need to be rude,’ retorted Isabel" "He refused to retort to the rash question about his propensity for imbibing."}
	
	\subsubsection{\textcolor{brickred}{reticent} (adj)}
	reserved,
	withdrawn, not revealing one's thoughts or feelings readily.
	\textcolor{gold}{"she was extremely reticent about her personal affairs" "They may appear reticent about the bother and expense of altering their wardrobe, but they give \textbf{tacit} approval to the change by rushing to the department stores where they \textbf{jostle} each other to buy copies of the more expensive dresses."}
	
	\subsubsection{\textcolor{brickred}{tacit} (adj)}
	(VA p.48) implicit
	understood
	implied
	inferred.
	\textcolor{gold}{"your silence may be taken to mean tacit agreement" "His egregious behavior brought a tacit reproach  to his mother's eyes."}
	
	\subsubsection{\textcolor{brickred}{chicanery} (n) [shi·kei·nr·ee]}
	the use of deception or subterfuge to achieve one's purpose.
	\textcolor{gold}{"storylines packed with political chicanery" "The conclusion one might reach after observing how women countenance the arbitrary changes year after year is that they are naive or victims of some chicanery practiced by the clothing industry." "The reporter divulged the blatant chicanery involved in the awarding ofthe contract."}
	
	\subsubsection{\textcolor{brickred}{docile} (adj)}
	ready to accept control or instruction; submissive. compliant
	obedient,
	pliant.
	\textcolor{gold}{"they are so docile because they secretly enjoy the yearly excitement around the latest fashions." "a cheap and docile workforce" "Even the most docile person may become fractious when he gets only a pittance for his hard labor."}\\\\
	- You hit the nail on the head when you said we ought to maintain the status quo and not change horses in midstream.
	
	\newpage
	\setcounter{section}{39}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{saga} (n) [saa·guh]}
	a long story of heroic achievement. (related to saw[3])
	\textcolor{gold}{"a figure straight out of a Viking saga" "An unforgettable saga of World War II has to do with the small French coastal town of Dunkirk." "The saga of a lone man confronting the turbulent oceans in a small boat is an \textbf{exploit} we find laudable."}
	
	\subsubsection{\textcolor{brickred}{belated} (adj)}
	coming or happening later than should have been the case. late, delayed, overdue, \textbf{tardy}.
	\textcolor{gold}{"a belated apology" "There, in 1940, thousands of British troops made a belated escape from the \textbf{awesome} power of the German army and air force." "The \textbf{ingrate} refused to accept Cindy's belated gift."}
	
	\subsubsection{\textcolor{brickred}{decrepit} (adj)}
	worn out or ruined because of age or neglect. \textbf{dilapidated}.
	\textcolor{gold}{"a row of decrepit houses" "hey were removed by an array of private boats, from huge yachts to decrepit fishing boats" "When released from incarceration, he was \textbf{gaunt and decrepit}"}
	
	\subsubsection{\textcolor{brickred}{\hl{imperturbable}} (adj) [im·pr·tur·buh·bl]}
	unable to be upset or excited; calm. poised,
	tranquil,
	serene,
	sedate,
	collected, \textbf{equanimous}.
	\textcolor{gold}{"an imperturbable tranquillity" "The speaker remained imperturbable while his audience shouted caustic comments about his mendacious activities." "They remained imperturbable under heavy fire."}
	
	\subsubsection{\textcolor{brickred}{vacillate} (v)}
	VA p.66. \textbf{dither},
	be indecisive/irresolute/undecided, waver
	\textbf{teeter},
	\textbf{temporize},
	hesitate,
	\textbf{oscillate},
	fluctuate.
	\textcolor{gold}{"I vacillated between teaching and journalism" "Once unloaded, they did not vacillate, but returned with equanimity to their vigil in the danger zone"}\\\\
	- \textbf{vessel} (n) = a ship/boat "When their vessels were loaded, they dashed back to England."\\
	- \textbf{ingrate} (n and adj) = ungrateful (person)\\
	- The British proved once again that they are paragons of comradeship in times of jeopardy.\\
	- to be in fine \textbf{fettle}(= codition)\\
	- \textbf{amiss} (adj/adv): not quite right; inappropriate or out of place.
	"there was something amiss about his calculations" "to see sth amiss with sth"
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{staunch} (adj)}
	1- very loyal and committed in attitude.
	2- (of a wall) of strong or firm construction.
	\textcolor{gold}{"a staunch supporter of the anti-nuclear lobby" "These are anathema to those values the staunch heroes would defend." "She is such a staunch friend, my reprehensible actions do not cause a schism between us."}
	
	\subsubsection{\textcolor{brickred}{opprobrium} (n) [uh·prow·bree·uhm]}
	1- harsh criticism or censure.
	2- public disgrace arising from shameful conduct.
	\textcolor{gold}{"The coach \textbf{heaped} opprobrium \textbf{upon}/\textbf{on} the fledgling ball player" "the critical opprobrium generated by his films" "the opprobrium of being closely associated with gangsters" "hey treat the lovely women with opprobrium, boo fucking hoo"}
	
	\subsubsection{\textcolor{brickred}{\underline{M}achiavellian} (adj)}
	cunning, scheming, and unscrupulous, especially in politics.
	\textcolor{gold}{"We are ready to rationalize Machiavellian activities on the part of our side if they are \textbf{to the detriment of} our adversary." "The \textbf{intrepid} (bi bak) heroes are  placed in  deleterious situations as a result of the \textbf{Machiavellian maneuvers} of their opponents."}
	
	\subsubsection{\textcolor{brickred}{uncon\underline{sc}i\underline{o}nable} (adj) [uhn·kaan·shuh·nuh·bl]}
	1- not right or reasonable. without \textbf{conscience}.
	2- unreasonably excessive.
	\textcolor{gold}{"the unconscionable conduct of his son" "shareholders have had to wait an unconscionable time for the facts to be established" "One unconscionable act of duplicity follows another until the total destruction of the "good  guys" seems at hand." "It was unconscionable to him to keep a book he had borrowed without making tenacious efforts to return it."}
	
	\subsubsection{\textcolor{brickred}{pandemonium} (n)}
	wild and noisy \underline{disorder} or confusion; uproar. bedlam.
	\textcolor{gold}{"there was complete pandemonium—everyone just panicked" "amidst (amid) the pandemonium of a battle" "There was pandemonium as the presidential nominee entered the convention site."}\\\\
	- However, evil is ubiquitous, and next week another fracas will erupt. 
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{flay} (v)}
	1- skin, excoriate, \textbf{strip} the skin off.
	2- criticize severely and brutally. scold harshly.
	\textcolor{gold}{"one shoulder had been flayed to reveal the muscles" "to flay the government for not moving fast enough on economic reform" "He would flay both the body and the spirit of anyone who crossed him." "He castigated his opponents and went to great lengths to flay them with accusations of megalomania."}
	
	\subsubsection{\textcolor{brickred}{demeanor} (n)}
	($\ne$ disposition/disposal) outward behavior or \underline{bearing}. conduct, \textbf{mien}, \textbf{deportment}.
	\textcolor{gold}{"a quiet, somber demeanor" "The crew developed such an aversion to Bligh's mortifying actions and demeanor that, they set him off in a lifeboat." "His demeanor was \textbf{atypical}; usually phlegmatic, he was belligerent and garrulous during the broadcast."}
	
	\subsubsection{\textcolor{brickred}{\hl{delineation}} (n) [di·li·nee·ei·shn]}
	portrayal,
	description,
	the action of describing or portraying something precisely.
	\textcolor{gold}{"the artist's \textbf{exquisite} delineation of costume" "Laughton's delineation 
		of Bligh remains as the image we have of him." "Then he gave an incisive delineation of his fulsome(?) opponents as an
		antiquated group, complacent about the noisome conditions in a moribund city."}
	
	\subsubsection{\textcolor{brickred}{vindicate} (v)}
	1- acquit,
	absolve,
	free from blame,
	declare innocent,
	exonerate,
	exculpate,
	discharge,
	redeem,
	let off.
	2- show or prove to be right, reasonable, or justified.
	justify,
	warrant,
	substantiate.
	\textcolor{gold}{"The mayor tried to vindicate his capricious and irrational actions" "more sober views were vindicated by events" "hospital staff were vindicated by the inquest verdict" "Only recently has any attempt been made to vindicate him."}
	
	\subsubsection{\textcolor{brickred}{heinous} (adj)}
	utterly \underline{odious} or wicked.
	\textcolor{gold}{"\textbf{a battery of} heinous crimes" ""The most heinous thing I have done," he said in a \textbf{stentorian} voice, was \textbf{eradicating} the truth" "his heinous reputation permeating history."}\\\\
	- the \textbf{mutiny} that \textbf{erupted} aboard that ship was the basis for a film.\\
	- an awesome bully and an \textbf{unmitigated} villain.\\
	- exquisite (adj): extremely beautiful and, typically, delicate.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{turpitude} (n)}
	depravity (=== moral corruption); wickedness. vileness.
	\textcolor{gold}{"acts of moral turpitude" "Historians maintain that there was no turpitude in Bligh's actions aboard the H.M.S." "From any facet of his life, the acme of moral turpitude was reached by Hitler."}
	
	\subsubsection{\textcolor{brickred}{infraction} (n)}
	a violation or \underline{infringement} of a law or agreement. violation. transgression.
	\textcolor{gold}{"We do not condone or tolerate an infraction of even the most trivial kind." "While an infraction aboard ship was quickly 
		criticized, Bligh never carried out those \textbf{callous} actions the 
		movie dramatized in order to depict an evil man, \textbf{say} his 
		defenders."}
	
	\subsubsection{\textcolor{brickred}{callous} (adj)}
	%\label{sec:callous}
	heartless,
	\underline{unfeeling},
	uncaring,
	cold, showing or having an insensitive and cruel disregard for others.
	\textcolor{gold}{"his callous comments about the murder made me shiver" "It takes a person to watch with equanimity as a gullible, naive girl falls for the line of a loathsome boy."}
	
	\subsubsection{\textcolor{brickred}{redress} (n/v)}
	(n) compensation,
	reparation,
	restitution,
	recompense,
	repayment. remedy or compensation for a wrong or grievance.
	(v) remedy or set right (an undesirable or unfair situation). rectify.
	\textcolor{gold}{"those seeking redress for an infringement of public law rights" "This \textbf{prodigious feat} alone, say those who would 
		restore Bligh's good name, should be enough to allow for a full 
		redress of the wrongs that have been blamed on him for over 
		150 years." "There seems to be no way to redress a grievance against at omnipotent 
		ruler."}
	
	\subsubsection{\textcolor{brickred}{vituperation} (n)}
	opprobrium, invective. bitter and abusive language.
	\textcolor{gold}{"no one else attracted such vituperation from him" "an end to \textbf{the vituperation heaped upon him} for these many years"}\\\\
	
	- While the \textbf{coterie} defending Captain Bligh do not 
	ask the public to praise him, they do request a more 
	\textbf{benevolent} attitude toward this traditionally reprehensible 
	figure.
	
	\newpage
	\setcounter{section}{40}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{rhetoric} (n) [reh·tr·uhk]}
	1- the art of effective/persuasive speaking/writing, especially the use of figures of speech and other compositional techniques. oratory, eloquence.\\
	2- language designed to have a persuasive/impressive effect on its audience, but often regarded as lacking in sincerity/meaningful content. 
	bombast, 
	loftiness, 
	turgidity, 
	grandiloquence, 
	magniloquence, 
	ornateness.
	\textcolor{gold}{"he is using a common figure of rhetoric, hyperbole" "They can maintain a fervid flow of rhetoric for hours at a time." "all we have from the Opposition is empty rhetoric" "At a time that requires tangible proposals, all he offers is unconscionable rhetoric"}
	
	\subsubsection{\textcolor{brickred}{clique} (n) [kleek]}
	a small, exclusive group of people. coterie.
	\textcolor{gold}{"the old-school clique" "It is not long before a young star has a clique around him who sporadically get their names into the newspapers."}
	
	\subsubsection{\textcolor{brickred}{extol} (v)}
	($\approx$ exalt $\neq$ exult = rejoice) praise enthusiastically.
	\textcolor{gold}{"he extolled the virtues of the Russian peoples" "they have \textbf{dispersed leaflets}, put up posters, and sent out cars and trucks with loudspeakers to extol the erudite qualities of their candidate." "Youngsters scoff when their elders extol the halcyon days of long ago."}
	
	\subsubsection{\textcolor{brickred}{mentor} (n)}
	tutor,
	coach, an experienced and trusted adviser.
	\textcolor{gold}{ "to come forward to shake the hand of their mentor."}
	
	\subsubsection{\textcolor{brickred}{facile} (adj) [fa·sl]}
	1- appearing neat and comprehensive only by ignoring the true complexities of an issue; superficial. simplistic.
	2- easily achieved; effortless.
	\textcolor{gold}{"a facile victory" "facile generalizations" "Now, with the facile solutions to complex problems carefully memorized, the show is ready to begin."}\\\\
	- One moment \textbf{facetious}, the next moment \textbf{profound}, the candidate works to \textbf{convince the} incredulous among the voters.\\
	- Amidst the adulation of the throng.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{\hl{cant}} (n)}
	(Not related to recant) insincere, hypocritical and sanctimonious talk, typically of a moral/religious/political nature.
	\textcolor{gold}{"he had no time for the cant of the priests about sin" "The diplomat was astute enough to see through the cant of the Machiavellian ambassador." "His public speeches may contain many cant phrases, but a sharp question by an astute reporter can destroy a cliche filled statement."}
	
	\subsubsection{\textcolor{brickred}{umbrage} (n)}
	VA p.309.
	\textcolor{gold}{"she took umbrage at his remarks" "Perhaps he will take umbrage at a suggestion that he favors the \textbf{affluent}." "I was flabbergasted when he took umbrage at my whimsical remarks."}
	
	\subsubsection{\textcolor{brickred}{magnanimous} (adj)}
	generous or forgiving, especially toward a rival or less powerful person.
	\textcolor{gold}{"we should be magnanimous in victory" "A somber examination of those indigent families, bereft of hope, sunken in apathy, should motivate us to be more magnanimous in our attempts to improve their lot." "His record is searched for evidence that he has been equally magnanimous to the indigent."}
	
	\subsubsection{\textcolor{brickred}{vilify} (v)}
	berate,
	disparage,
	denigrate,
	malign,
	slander.
	\textcolor{gold}{"he has been vilified in the press" "He accuses the reporter of attempting to vilify him."}
	
	\subsubsection{\textcolor{brickred}{elucidate} (v)}
	(from lucid) make clear; explain.
	\textcolor{gold}{"work such as theirs will help to elucidate this matter" "They insist that he elucidate positions that the politician would rather leave in a nebulous state."}\\\\
	- The television press interview is \textbf{conducive} to close scrutiny of a candidate.\\
	- The press wants to allude to things that keep him in the midst of controversy.\\
	mainstay (n) =\textgreater "farming is the mainstay of the rural economy" "a Mainstay of Opera Star's repertoire"
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{vapid} (adj)}
	insipid, zestless, sterile,
	anaemic [uh·nee·muhk] (anaemia),
	tame,
	bloodless,
	jejune,
	vacuous,
	bland,
	stale,
	trite,
	pallid,
	wishy-washy, offering nothing that is stimulating or challenging.
	\textcolor{gold}{"As \textbf{a concomitant to} his belligerent and vituperative antipathy toward his government. he became an expatriate, but he found it a vapid life." "tuneful but vapid musical comedies" "While we are all cognizant of the importance of words to create certain impressions, gesture is  relegated  to  a  much lesser role. Gestures are an  important \textbf{concomitant} to even the most vapid speech."}
	
	\subsubsection{\textcolor{brickred}{unwieldy} (adj)}
	cumbersome, bulky. difficult to handle/move because of its size, shape, or weight. - (of a system) too large or disorganized to function efficiently.
	\textcolor{gold}{"Kyra was so disgruntled about having to move the unwieldy piano. she procrastinated for days." "the benefits system is unwieldy and unnecessarily complex" "a class at a university, unwieldy because of its large size, was split up."}
	
	\subsubsection{\textcolor{brickred}{proximity} (n)}
	propinquity, nearness, contiguity,
	vicinity === vicinage.
	\textcolor{gold}{"do not operate microphones in proximity to television sets" "One group was put into a room in proximity to good loudspeakers. Every nuance of the lecturer's voice could be heard clearly." "As the \textbf{scion} of  an  affluent family, he was often in proximity to opulence."}
	
	\subsubsection{\textcolor{brickred}{lassitude} (n)}
	lethargy,
	listlessness,
	weariness,
	languor,
	sluggishness,
	enervation,
	exhaustion,
	fatigue,
	drowsiness,
	torpor,
	torpidity,
	ennui [aan·wee],
	lifelessness,
	sloth,
	apathy. 
	\textcolor{gold}{"After playing with his progeny in \textbf{the enervating sun} he was overcome by lassitude and retired to bed/staggered back to his room" "they soon  took  on the appearance of  extreme lassitude"}
	
	\subsubsection{\textcolor{brickred}{vitiate} (v)}
	VA p.454.
	\textcolor{gold}{"development programmes have been vitiated by the rise in population" "The separation of visual and \textbf{aural} [aw·ruhl] communication tended to vitiate the learning process." "The irrelevant evidence seemed to vitiate the prosecutor's case and precluded a conviction."}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{augment} (v)}
	\textcolor{gold}{"he augmented his summer income by painting houses" "With actresses, gesture serves much more than merely to augment speech." "The parsimonious octogenarian sought to augment his wealth by removing it from its cache and placing it in a bank."}
	
	\subsubsection{\textcolor{brickred}{fatuous} (adj) [fa·choo·uhs]}
	silly and pointless. inane, nonsensical,
	childish,
	puerile,
	infantile,
	asinine,
	daft.
	\textcolor{gold}{"a fatuous comment" "To show that he was distraught about the danger in which the heroine had been placed, the hero would go through the most fatuous actions. He would stagger, beat his breast, tear his hair, and contort his face into the most  doleful appearance." "his obsequious desires led to the most fatuous behavior."}
	
	\subsubsection{\textcolor{brickred}{contort} (v)}
	\underline{twist}/bend out of the normal shape.
	\textcolor{gold}{"a \textbf{spasm} of pain contorted his face" "The paroxysm of coughing served to contort her body until she could gain a respite."}
	
	\subsubsection{\textcolor{brickred}{repertoire} (n) [reh·puh·twaar]}
	works that an artist is ready to perform, a stock of skills or types of behaviour that a person habitually uses.
	\textcolor{gold}{"her repertoire of denigratory (\textbf{denigrate} = disparage) gestures" "There weren't many simple or restrained gestures in his repertoire." "Her virtuosity (skill) was demonstrated by the works she performed from her repertoire"}
	
	\subsubsection{\textcolor{brickred}{imperceptible} (adj)}
	so slight, gradual, or subtle as not to be perceived.
	\textcolor{gold}{"almost imperceptible changes in facial expression that could transmit nuances of emotion" "his head moved in an almost imperceptible nod" "He had always appeared virile, so that the imperceptible decline toward senility went unnoticed until he succumbed and began to use a cane."}\\\\
	spasm = convulsion,
	contraction.\\
	- He must weigh carefully each and every \textbf{utterance}.\\
	- "his \textbf{reserve} was not intended as a rebuff"
	
	\newpage
	\setcounter{section}{41}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{curry} (v) (to curry favor)}
	ingratiate oneself with someone through obsequious behavior. to seek favor by flattery.
	\textcolor{gold}{"a \textbf{wimpish} (weak, cowardly) attempt to \textbf{curry favor with} the new bosses" "He discreetly tried to \textbf{curry favor with} his employer" "They spend huge sums developing new products with which to curry her favor."}
	
	\subsubsection{\textcolor{brickred}{\hl{pall}} (v)}
	become less appealing or interesting through familiarity. cease to please, become dull.
	\textcolor{gold}{"the novelty of the quiet life palled" "Those conditions were not conducive to a felicitous evening as the dance would soon pall for the lack of feminine companionship." "Fearful that a successful product will soon begin to palL the manufacturers, without cessation, come out with "new and improved" versions to  \textbf{whet  her appetite/desire, /interest}."}
	
	\subsubsection{\textcolor{brickred}{succulent} (adj)}
	(of food) tender, \underline{juicy}, and tasty.
	\textcolor{gold}{ "a colorful photo of a succulent meal/steak on a TV dinner box."}
	
	\subsubsection{\textcolor{brickred}{satiety} (n) [suh·tai·uh·tee]}
	\textbf{VA 216}. excess, overly full, surfeit. the feeling or state of being \textbf{sated}.
	\textcolor{gold}{"The host exhorted his guests to eat to satiety" "the housewife is faced with a satiety of merchandise"}
	
	\subsubsection{\textcolor{brickred}{intrinsic} (adj)}
	belonging naturally; essential. inherent.
	\textcolor{gold}{"access to the arts is intrinsic to a high quality of life" "Particularly in the copiously stocked laundry detergent section. While there may be almost no intrinsic difference among the many brands, advertising and packaging serves to \textbf{importune} her to buy one rather than another."}\\\\
	- \textbf{survey} (v) =\textgreater look closely at or examine (sb or sth). (\textbf{surveillance}) "her green eyes surveyed him coolly" "The American housewife is queen of all she surveys in the supermarket."\\
	- She coveted the antiquated locket.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{\hl{potpourri}} (n) [pow·pr·ee]}
	a \underline{mixture} or \underline{medley} [med·lee] of things. farrago. \textbf{miscellany}, \textbf{melange} [muh·laanj].
	\textcolor{gold}{"he played a potpourri of tunes from Gilbert and Sullivan" "Walking up and down the aisles of a supermarket, one seldom stops to analyze the individual package in  the potpourri of items on  the shelves." "A potpourri of today's musical hits sounds more like cacophony than \textbf{harmony}."}
	
	\subsubsection{\textcolor{brickred}{sanction} (v/n)}
	(give) official permission or approval for (an action). endorse.
	\textcolor{gold}{"I cannot sanction your lax attitude towards the imminent threat of a conflagration." "the scheme was sanctioned by the court" "he appealed to the bishop for his sanction" "Before he will sanction the use of a particular can, box, or bottle, he must know many things about its efficacy."}
	
	\subsubsection{\textcolor{brickred}{denote} (v)}
	be a sign of; indicate. designate, signify.
	\textcolor{gold}{"His levity at such a serious moment denotes a lack of feeling. " "this mark denotes purity and quality" "a white box may denote cleanliness, a red one, strength."}
	
	\subsubsection{\textcolor{brickred}{allude} (v)}
	\underline{suggest} or call attention to indirectly; hint at.
	\textcolor{gold}{"You can be sure the candidate will allude to the moribund state of our economy and offer his panacea." "she had a way of alluding to Jean but never saying her name" "There may be a photo or a drawing that will allude to the product's use or special qualities."}
	
	\subsubsection{\textcolor{brickred}{insidious} (adj)}
	proceeding in a gradual, subtle way, but with very harmful effects.
	\textcolor{gold}{"feminism is a serious and insidious problem" "In some insidious way the glib salesman played upon my repressed desires and sold me a gaudy sports car."}\\\\
	- The manufacturer had to glean and test many different designs before he accepted the one you see in the array before you.\\
	- \textbf{plagiarize} (v) [plei·jr·aiz]: take (the work/an idea of sb else) and pass it off as one's own. "he was fined 6,000 bucks for having plagiarized the song" "the author claims she was plagiarized"
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{propriety} (n) [pruh·prai·uh·tee]}
	the condition of being right, appropriate, or fitting. \underline{correctness}, \underline{suitability}. conformity to conventionally accepted standards of behaviour or morals.
	\textcolor{gold}{"they questioned the propriety of certain investments made by the council" "Few question the propriety of the current haste on the part of manufacturers to bring out "new and improved" products" "he always behaved with the utmost propriety" "We question the propriety of making fun of obese people."}
	
	\subsubsection{\textcolor{brickred}{advent} (n)}
	the \underline{arrival} of a notable person/thing. emergence, materialization, surfacing, coming.
	\textcolor{gold}{"At one time, in the dim, distant past before the advent of television." "With the advent of text messaging, Roger was busy night and day."}
	
	\subsubsection{\textcolor{brickred}{\hl{impious}} (adj) [uhm·pai·uhs]}
	showing a lack of respect for God or religion. wicked.
	\textcolor{gold}{"the emperor's impious attacks on the Church" "impious villains" "In the milieu of city street life it is not atypical to hear impious comments about authority."}
	
	\subsubsection{\textcolor{brickred}{proffer} (v)}
	offer, hold out or put forward (sth) to sb for acceptance.
	\textcolor{gold}{"she proffered a glass of wine" "I'd like to proffer my belated congratulations on your 25 years of married serenity." "Year after year, the local grocery store owner would proffer the same box of cereal,"}
	
	\subsubsection{\textcolor{brickred}{\hl{spate}} (n)}
	a large number of similar things coming in quick \underline{succession}. series.
	\textcolor{gold}{"A few years ago there was a spate of science-fiction films about awesome monsters causing pandemonium on our planet, but after a surfeit of that genre, their popularity began to \textbf{wane}." "a spate of attacks on holidaymakers" "Today's spate of transient products would have been considered an anomaly in those days."}\\\\
	- \textbf{irreverent}\\
	- Supermarkets overcome this encumbrance by making these brands less expensive.\\
	- \textbf{ratify} (v) : sign or give formal consent to (a treaty, contract, or agreement), making it officially valid. confirm. "both countries were due to ratify the treaty by the end of the year"
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{shibboleth} (n) [shi·buh·leth]}
	a custom, principle, or belief distinguishing a particular class or group of people, especially a long-standing one regarded as outmoded or no longer important.
	\textcolor{gold}{"the majority, under the influence of vague nineteenth-century shibboleths, understood him to be associating himself with the doctrine that every nation has a right to be a sovereign state" "Many people believe the shibboleth, "You get what you pay for," and they purchase items on the premise that quality varies as the price does." "People often try to compensate for their deplorable lack of culture by repeating the shibboleth , "I know what I like.""}
	
	\subsubsection{\textcolor{brickred}{bogus} (adj)}
	not genuine or true (used in a disapproving manner when deception has been attempted). fake, spurious, fraudulent, counterfeit, sham.
	\textcolor{gold}{"a bogus insurance claim" "Are the claims made  by  nationally advertised brands bogus?" "He had the audacity to try to \textbf{foist} (impose) a bogus dollar on me."}
	
	\subsubsection{\textcolor{brickred}{substantiate} (v)}
	provide evidence to support or prove the truth of. prove, justify, vindicate, validate, corroborate.
	\textcolor{gold}{"they had found nothing to substantiate the allegations" "How can one bread company substantiate its \textbf{nutritive} superiority over another?" "The reporter wanted to elicit the pertinent facts from the reticent witness so he could substantiate the charge of moral turpitude against the high city official."}
	
	\subsubsection{\textcolor{brickred}{nutritive} (adj) [noo·truh·tuhv]}
	1- relating to nutrition.\\
	2- providing nourishment; nutritious.
	\textcolor{gold}{"the food was low in nutritive value" "nutritive food"}
	
	\subsubsection{\textcolor{brickred}{\hl{raucous}} (adj) [raa·kuhs]}
	(ruckus) making or constituting a disturbingly \underline{harsh} and loud noise. strident. shrill.
	\textcolor{gold}{"raucous youths" "They make \textbf{inordinate} (excessive) claims, using those raucous techniques proven so successful in convincing the frugal consumer to switch to a more costly brand." "There were raucous complaints about the inordinate number of fatal accidents caused by inebriated drivers."}
	
	\newpage
	\setcounter{section}{42}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{quandary} (n)}
	a \underline{state of perplexity/uncertainty} over what to do in a difficult situation. \underline{dilemma}, plight, predicament. sticky situation.
	\textcolor{gold}{"The consumer is \textbf{in a quandary} about making a felicitous selection among the array of products." "a legal quandary"}
	
	\subsubsection{\textcolor{brickred}{callous} (adj)} %\hyperref[sec:callous]
	\textcolor{gold}{"Who can be about the presence of many indigent families in proximity to affluence?" "The advertisers must influence the malleable consumer, and often they do it in the most callous ways."}
	
	\subsubsection{\textcolor{brickred}{\hl{expedient}} (adj)}
	suitable or appropriate. \underline{convenient} and practical although possibly improper or immoral.
	\textcolor{gold}{"either side could break the agreement if it were expedient to do so" "The advertiser knows that a television commercial is the most expedient way to reach large numbers of people." "Because she had committed only a venial offense, he thought it expedient to \textbf{abjure} a severe punishment." "holding a public enquiry into the scheme was not expedient"}
	
	\subsubsection{\textcolor{brickred}{negligible} (adj)}
	\textbf{trifling}, \textbf{inconsequential}, trivial
	insignificant.
	\textcolor{gold}{"he said that the risks were negligible" "The cost for each commercial film is prodigious, but because the audience is so large, the cost per viewer is negligible."}
	
	\subsubsection{\textcolor{brickred}{blasé} (adj)}
	unimpressed with or \underline{indifferent} to something because one has experienced or seen it so often before. insouciant, glutted, cloyed, satiated, pococurante.
	\textcolor{gold}{"Each commercial is prepared in the most meticulous way in order to catch the attention of even the most blasé viewer and hold it until the message is through." "she was becoming quite blasé about the dangers"}\\\\
	- \textbf{exhume} (v)\\
	- \textbf{deluge} (v/n)\\
	- It \textbf{did my heart good} to see that \textbf{inveterate} egotist \textbf{eat humble pie}.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{ennui} (n) [aan·wee]}
	boredom, \textbf{tedium}, lethargy, lassitude, \textbf{languor}, a feeling of \underline{listlessness} and dissatisfaction arising from a lack of occupation or excitement.
	\textcolor{gold}{"The fledgling pianist knew that his mentor would take umbrage at his yawning during the lesson, but the feeling of ennui was overwhelming." "he succumbed to ennui and \textbf{despair}" "Some television commercials, trying to break through the ennui built up in the viewer by the plethora of competition, employ humor."}
	
	\subsubsection{\textcolor{brickred}{comely} (adj)}
	pleasant to look at; attractive (typically used of a woman).
	\textcolor{gold}{"the comely Italian actress Valeria Golino" "to feature a comely girl as a \textbf{pretext} for getting the viewer to stay tuned in."}
	
	\subsubsection{\textcolor{brickred}{frenetic} (adj) [fruh·neh·tuhk]}
	frantic,
	frenzied,
	hectic, fast and energetic in a rather wild and uncontrolled way.
	\textcolor{gold}{"a frenetic pace of activity" "At times raucous music, accompanied by some frenetic activities, is designed to preclude the viewer's loss of attention." "They were vigilant in order that their \textbf{surreptitious} meetings would not be discovered, and it often required frenetic changes of plans to preclude exposure."}
	
	\subsubsection{\textcolor{brickred}{artifice} (n) [aar·tuh·fuhs]}
	trickery, deviousness, deceit, subterfuge, strategy. clever or cunning devices or \textbf{expedients}, especially as used to trick or deceive others.
	\textcolor{gold}{"an industry dominated by artifice" "The advertiser will employ every bit of artifice at the film maker's command to make a \textbf{trenchant} commercial." "They furtively employed every kind of artifice to ..."}
	
	\subsubsection{\textcolor{brickred}{diversity} (n) [duh·vur·suh·tee]}
	variety, the state of being diverse. miscellany.
	\textcolor{gold}{"The diversity of appeals made to the viewer is \textbf{a concomitant of} the many ways people react to commercials." "there was considerable diversity in the style of the reports" "newspapers were \textbf{obliged} to allow a diversity of views to be printed" "He employed all of his rhetoric to vilify those who would be brash enough to suggest that a of diversity opinions should be expressed."}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{qualm} (n) [kwaam]}
	pang/twinge of conscience/remorse. an uneasy feeling of doubt, worry, or fear, especially about one's own conduct; a \underline{misgiving}.
	\textcolor{gold}{"military regimes generally have no qualms about controlling the press" "They do not have the slightest qualm about questioning the consumer about personal things in her own domicile." "He had a serious qualm about hunting for the nearly extinct quarry."}
	
	\subsubsection{\textcolor{brickred}{expurgate} (v)}
	VA 366.
	\textcolor{gold}{"editors heavily expurgated the novel before its initial publication" "to expurgate one's answers."}
	
	\subsubsection{\textcolor{brickred}{begrudge} (v)}
	1- give reluctantly or \underline{resent}fully.
	2- envy (sb) the possession or enjoyment of (sth).
	\textcolor{gold}{"nobody begrudges a single penny spent on health" "she begrudged Martin his affluence" "Generally, people are  not reticent and do not begrudge giving the time and effort" "She did not begrudge paying the pittance extra for a better coat."}
	
	\subsubsection{\textcolor{brickred}{artless} (adj)}
	without effort or pretentiousness; natural and simple. without guile or deception.
	\textcolor{gold}{"an artless, naive girl" "an artless literary masterpiece" "The questions \textbf{delve} (dig) rather deeply, and what the artless responses divulge will help the advertiser." "the artless comments of young children"}
	
	\subsubsection{\textcolor{brickred}{gratuity} (n) [gruh·too·uh·tee]}
	a tip.
	\textcolor{gold}{ "The interviewer usually offers no gratuity to the person who has helped, but often a sample of the product is proffered as thanks." "He took umbrage when I offered a gratuity to augment his small salary."}\\\\
	- \textbf{efficacious}\\
	- the copious results make it feasible to prognosticate how well the commercial will do.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{manifest} (adj)}
	clear or \underline{obvious} to the eye or mind. evident. apparent,
	patent,
	palpable.
	\textcolor{gold}{"t was manifest that an arbiter would be needed because neither side would capitulate to a plan \textbf{foisted} on them by the other side." "her manifest charm and proven ability" "... makes it manifest that ..."}
	
	\subsubsection{\textcolor{brickred}{delve} (v)}
	dig, investigate.
	\textcolor{gold}{"If we delve below and behind the rhetoric and invective, we may discover the profound reasons for the \textbf{ferment} in our land." "she delved in her pocket" "the society is determined to delve deeper into the matter" "This has helped the advertiser delve deeply into what motivates people"}
	
	\subsubsection{\textcolor{brickred}{capricious} (adj)}
	whimsical, fickle, inconstant, mercurial, erratic.
	\textcolor{gold}{"it's terrible to feel our livelihood hinges on a capricious boss" "a capricious climate" "The advertising agency is never capricious and can vindicate spending large sums of money on research." "When the acrimonious discussion about his capricious actions had attenuated, he was able to vindicate his conduct."}
	
	\subsubsection{\textcolor{brickred}{requisite} (n/adj) [reh·kwuh·zuht]}
	made \underline{necessary} by particular circumstances or regulations. a thing that is necessary for the achievement of a specified end. required, requirement, prerequisite
	\textcolor{gold}{"the application will not be processed until the requisite fee is paid" "he believed privacy to be a requisite for a peaceful life" "Having uncovered what the public wants, the advertiser expedites putting the requisite words, music, and photographs of the product on film." "One mortifying requisite for the position was that he would have to work for one year under \textbf{the aegis of a fatuous egotist}."}
	
	\subsubsection{\textcolor{brickred}{replenish} (v)}
	refill, restock
	\textcolor{gold}{"he replenished Justin's glass with mineral water" "all creatures need sleep to replenish their energies" "He will thus replenish the never-ending, ubiquitous television commercial supply in the hope that the consumer will remember some facet of the film and buy the product."}
	
	\newpage
	\setcounter{section}{43}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{roster} (n)}
	\textcolor{gold}{"The coach knew he would have to add experienced players to the roster to \textbf{compensate for the spate of} freshmen on the team." "next week's duty roster" "a cluster of outstanding players on the club's roster" "If one were to look at the roster of physical handicaps, one would reach the somber conclusion that  the list is a long one." "the locomotive is rostered for service on Sunday"}
	
	\subsubsection{\textcolor{brickred}{stunted} (adj)}
	stunt (v) : prevent from growing or developing properly. small, little, undersized.
	\textcolor{gold}{"There seems to be \textbf{voluminous} evidence that the mother's smoking will stunt the baby's growth." "the trees exhibit a stunted appearance" "some weeds produce chemicals that stunt the plant's growth" "stunted development of an arm or leg due to a  birth anomaly."}
	
	\subsubsection{\textcolor{brickred}{atrophy} (v) [a·truh·fee]}
	gradually decline in effectiveness/vigor due to underuse/neglect.
	\textcolor{gold}{"The prodigy allowed his musical talent to atrophy as he redirected his career." "the imagination can atrophy from lack of use" "a crippling disease that has caused muscles to atrophy."}
	
	\subsubsection{\textcolor{brickred}{maim} (v) [meim]}
	\underline{wound}/\underline{injure} so that part of the body is permanently damaged.
	\textcolor{gold}{"100,000 soldiers were killed or maimed" "illnesses and injuries that maim and \textbf{debilitate} (weaken)." "When it seemed that Reggie would maim his opponent, we broke upthe fight."}
	
	\subsubsection{\textcolor{brickred}{ameliorate} (v) [uh·mee·lee·ur·eit]}
	make better. improve. enhance.
	\textcolor{gold}{"If you heap opprobrium on an impious child, it probably will not ameliorate the conditions that led to the rebelliousness." "the reform did much to ameliorate living standards" "Modern medicine has done much to ameliorate the physical problems."}\\\\
	- People are not naturally callous, but in some perverse way they have \textbf{the propensity to repress} any concern with the  physically handicapped. The social problems seem to be inherent in our own attitudes.\\
	- alleviate = assuage
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{cynic} (n)}
	1- a person who believes that people are motivated purely by self-interest rather than acting for honorable or unselfish reasons.
	2- pessimist, skeptic. a person who questions whether something will happen or whether it is worthwhile.
	\textcolor{gold}{"some cynics thought that the controversy was all a publicity stunt" "The obstacles that frustrate the physically handicapped person who is seeking employment may turn him into a cynic." "the cynics were silenced when the factory opened"}
	
	\subsubsection{\textcolor{brickred}{unctuous} (adj)}
	excessively \underline{flattering} or \underline{ingratiating}; oily. sycophantic, obsequious,
	fawning,
	servile,
	subservient.
	\textcolor{gold}{"he seemed anxious to please but not in an unctuous way" "a prospective employee, with a rather unctuous manner" "We had to \textbf{wince} as we watched the newcomer try to wheedle and ingratiate himself into the teacher's favor in the most unctuous manner."}
	
	\subsubsection{\textcolor{brickred}{benevolent} (adj)}
	well meaning and \underline{kindly}. also, \underline{charitable}.
	\textcolor{gold}{"he was something of a benevolent \textbf{despot} (\textbf{tyrant}, dictator)" "The employer appears to be acting in a benevolent manner, but this attitude shows no compassion, for he really expects the person seeking the job to remain \textbf{subservient}."}
	
	\subsubsection{\textcolor{brickred}{subservient} (adj)}
	prepared to obey others unquestioningly. servile, submissive,
	deferential,
	acquiescent,
	compliant,
	accommodating,
	obedient, obsequious.
	\textcolor{gold}{"she was subservient to her parents" "While his demeanor remained imperturbable, there was latent anger at the ignominious and subservient role he had to play."}
	
	\subsubsection{\textcolor{brickred}{iniquity} (n) [uh·ni·kwuh·tee]}
	immoral or grossly unfair behavior. wickedness.
	\textcolor{gold}{"a den of iniquity" "This iniquity cannot but give the handicapped a feeling that they are being discriminated against."}\\\\
	- He does not expect a sinecure, but he has an aversion to the prevalent belief that he should consider himself lucky to find any employment. 
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{largess} (n)}
	VA. 406. generosity,
	liberality,
	munificence,
	bounty,
	bountifulness,
	beneficence.
	\textcolor{gold}{"presumably public money is not dispensed with such largesse to anyone else" "The offering of employment should not be considered a largess." "the distribution of largesse to the local population" "He felt it would be ignominious for him to accept any largess from the charlatan whose Machiavellian schemes had made him affluent."}
	
	\subsubsection{\textcolor{brickred}{criterion} (n)}
	basis, a principle or \underline{standard} by which something may be judged or decided.
	\textcolor{gold}{"they award a green label to products that meet certain environmental criteria" "The only criterion should be what he is capable of doing."}
	
	\subsubsection{\textcolor{brickred}{repent} (v)}
	regret, rue, be penitent
	\textcolor{gold}{"the Padre urged his listeners to repent" "he will not repent his having tried something new just to \textbf{mollify} his conscience." "After every election we repent, in a belated criticism, the apathy and complacency of so many people who failed to vote."}
	
	\subsubsection{\textcolor{brickred}{mollify} (v)}
	\underline{appease} the anger or anxiety of (someone). placate, pacify, conciliate.
	\textcolor{gold}{"nature reserves were set up around the power stations to mollify local conservationists" "When Mother is in a pique about some infraction of a rule, it takes all of our dexterity to mollify her."}
	
	\subsubsection{\textcolor{brickred}{mercenary} (adj)}
	\textcolor{gold}{"she's nothing but a mercenary little gold-digger" "Even for the most mercenary employer, there should be no reticence in eliciting the best that is possible from the handicapped worker." "Behind the facade of ostensible  benevolence there was a mercenary streak."}\\\\
	- No one who understands their needs can \textbf{condone} this attitude.\\
	- The \textbf{windfall} from his distant cousin came like a bolt from the blue. 
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{pariah} (n) [pr·ai·uh]}
	VA. 378. an outcast.
	\textcolor{gold}{"they were treated as social pariahs" "Socially, the handicapped person is often treated as a pariah." "He was stigmatized as a pariah when he had the audacity to boast of his nefarious and sordid career printing bogus money."}
	
	\subsubsection{\textcolor{brickred}{aloof} (adj)}
	not friendly or forthcoming; cool and \underline{distant}. reserved.
	\textcolor{gold}{"they were \textbf{courteous} but \textbf{faintly} aloof" "he stayed aloof from the bickering" "Although many people say this is a \textbf{propitious} (favorable) time to invest in the stock market,there is a tenable argument for remaining aloof" "Most people hold themselves aloof from normal contact with those who are different."}
	
	\subsubsection{\textcolor{brickred}{pragmatic} (adj)}
	VA. 13. practical. dealing with things sensibly and realistically in a way that is based on practical rather than theoretical considerations.
	\textcolor{gold}{ "they would learn in a pragmatic way that these are people who happen to have a physical handicap"}
	
	\subsubsection{\textcolor{brickred}{vestige} (n) [veh·stuhj]}
	a \underline{trace} or remnant of something that is disappearing or no longer exists.
	\textcolor{gold}{"the last vestiges of colonialism" "As long as there is a vestige of feeling that handicapped people are inferior, then we are all handicapped in one way or another." "After therapy, there remained hardly a vestige of his phobia"}
	
	\subsubsection{\textcolor{brickred}{guise} (n) [guys :)]}
	(disguise) an external form, appearance, or manner of presentation, typically concealing the true nature of something.
	\textcolor{gold}{"he visited in the guise of an inspector" "Under the guise of physical superiority we demonstrate a moral turpitude that is harmful to all." " In the guise of maintaining national unity under military rule, there was a paucity of even \textbf{innocuous dissen}t."}\\\\
	- The iniquity of assuming that physical superiority equals moral superiority prevents all of us from direct human relationships.
	
	\newpage
	\setcounter{section}{44}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{nullify} (v)}
	1- make of no use or value; cancel out. neutralize, negate, render ineffective.
	2- invalidate, annul, abolish, abrogate, rescind.
	\textcolor{gold}{"insulin can block the release of the hormone and \textbf{thereby} nullify the effects of training" "Natural disasters tend to nullify the best efforts of mankind." "In order to nullify the height advantage of his adversary, he \textbf{abjured} smoking and did an inordinate amount of exercise until he was the acme of litheness and dexterity."}
	
	\subsubsection{\textcolor{brickred}{deluge} (v/n)}
	flood. \underline{inundate} with a great quantity of something.
	\textcolor{gold}{"the country was deluged with rain" "he has been deluged with offers of work" "the waters that deluge our towns and cities, jeopardizing lives and culminating in the destruction of the results of endless work in the space of a few moments" "The office was deluged with requests for his autograph as the girls became cognizant of his identity."}
	
	\subsubsection{\textcolor{brickred}{futility} (n) [fyoo·ti·luh·tee]}
	pointlessness, fruitlessness or uselessness. vanity (1- conceit. 2- the quality of being worthless or \textbf{futile} [fyoo·tl].).
	\textcolor{gold}{"In spite of his efforts to cajole the girl, she remained aloof, and the futility of his efforts made him lugubrious." "the horror and futility of war" "We are all vulnerable to feelings of futility as we view the \textbf{carnage} caused to cattle from the sudden inundation."}
	
	\subsubsection{\textcolor{brickred}{carnage} (n)}
	slaughter, massacre, pogrom
	\textcolor{gold}{"We found it impossible to mollify the irate owner of three prize cats as he viewed the carnage caused by our large dog." "the bombing was timed to cause as much carnage as possible" ""}
	
	\subsubsection{\textcolor{brickred}{technology} (n)}
	\textcolor{gold}{"To our consternation, modern has made feasible \textbf{a spate of} lethal devices that could lead to the \textbf{inadvertent} destruction of the world." "Despite the laudable advances made in technology..."}\\\\
	- Disasters of this type, leaving only pathetic vestiges of homes and shops, are accepted as inevitable, and all we can do is to attempt to ameliorate the conditions that result.\\
	- One of the latent dangers \textbf{indigenous} to our...
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{libel} (n/v) [lai·bl]}
	a published false statement that is damaging to a person's reputation; a written \underline{defamation} [deh·fuh·mei·shn].
	\textcolor{gold}{"There are libel laws that protect against false charges." "she alleged the magazine had libeled her" "Publishers of newspapers and magazines \textbf{augment their staff} with lawyers to represent them when they are sued for libel"}
	
	\subsubsection{\textcolor{brickred}{defamatory} (adj)}
	(of remarks, writing, etc.) damaging the good reputation of someone; slanderous or libelous [lai·buh·luhs].
	defaming,
	calumnious,
	vilifying.
	\textcolor{gold}{"If an individual believes his character or livelihood have been damaged by a defamatory article/allegation, he can sue." "I resent your defamatory remark that depicts me as a culprit."}
	
	\subsubsection{\textcolor{brickred}{plaintiff} (n)}
	a person who brings a case against another in a court of law. the complaining party.
	\textcolor{gold}{"As the plaintiff he must \textbf{refute} the story and show how the defendant caused him harm by printing a \textbf{canard}." "the plaintiff commenced an action for damages" "The egregious calumny of the defendant worked to the advantage of the plaintiff"}
	
	\subsubsection{\textcolor{brickred}{canard} (n) [kuh·naard]}
	an unfounded rumor or story. a made-up sensational story.
	\textcolor{gold}{"the old canard that LA is a cultural wasteland" "The mayor vehemently denied there was any \textbf{antipathy} ($\neq$ apathy) between the governor and himself and blamed this on their political opponents."}
	
	\subsubsection{\textcolor{brickred}{deprecate} (v)}
	express disapproval of. disapprove of, deplore, abhor.
	\textcolor{gold}{"what I deprecate is persistent indulgence" "The cynic will deprecate the motives of anyone who tries \textbf{to ameliorate the iniquities} in our society." "We all deprecate a situation in which someone suffers"}\\\\
	- This would be tantamount to destroying \textbf{the efficacy of our coveted right to} learn the truth from the press.\\
	- Only when the harm is caused by someone with a desire \textbf{to malign under the guise of} printing the news can the individual expect to win \textbf{compensation} through the courts.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{reputed} (adj) [ruh·pyoo·tuhd]}
	(repute) supposed,
	putative,
	apparent,
	ostensible,
	suppositious,
	reputative.
	\textcolor{gold}{"a reputed budget of \$165 million" "he was a Danish philosopher who is reputed to be the forerunner of the current vogue of existentialism." "The drug is reputed to have a salubrious effect on nascent conditions of this type"}
	
	\subsubsection{\textcolor{brickred}{frail} (adj)}
	(of a person) weak and \textbf{delicate} (= 1- exquisite 2- easily broken/damaged; fragile.).
	\textcolor{gold}{ "In appearance he was a frail and ungainly man." "His awesome mental dexterity compensated for his frail physical condition."}
	
	\subsubsection{\textcolor{brickred}{potent} (adj) [pow·tnt]}
	(omnipotent) having great power, influence, or effect. powerful, strong, vigorous, mighty, formidable, influential.
	\textcolor{gold}{"thrones were potent symbols of authority" "An extremely erudite thinker and writer, he was a potent force in  propagating the new approach to  life." "When Ben's muscles began to atrophy, the doctor initiated therapy with  potent new drug."}
	
	\subsubsection{\textcolor{brickred}{excoriate} (v)}
	VA 426. criticize severely. censure, denounce, condemn, arraign, lambast, pillory, disapprove of, \textbf{carp}/cavil at, rail/inveigh against, cast aspersions on, pour scorn on, disparage, denigrate, deprecate, malign, vilify, besmirch, objurgate.
	\textcolor{gold}{"he excoriated the government for censorship" "His philosophy would excoriate those who believed that man could stand aside from life." "Even though she was piqued at his indolent manner, it was pathetic to listen to her excoriate him in public."}
	
	\subsubsection{\textcolor{brickred}{devout} (adj)}
	1- religious, pious. 2- totally \underline{committed} to a cause or belief. dedicated, devoted, loyal, faithful, \textbf{staunch}.
	\textcolor{gold}{"the most devout environmentalist" "she was a devout Catholic" "He was a religiously devout man who fervidly believed that the individual is always paramount." "Although he was a devout adherent of the party, he remained aloof during the \textbf{vitriolic} (\textbf{acrimonious}, \textbf{rancorous}, bitter, caustic, \textbf{mordant}, \textbf{acerbic}) primary campaign."}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{diminutive} (adj) [duh·mi·nyuh·tuhv]}
	extremely/unusually small. tiny, petite, miniature, minuscule.
	\textcolor{gold}{"a diminutive figure dressed in black" "The saga of the introduction of that diminutive song bird, the canary, into the homes of the world as \textbf{tame} (domesticated, domestic, docile) pets is an interesting one."}
	
	\subsubsection{\textcolor{brickred}{profuse} (adj) [pruh·fyoos]}
	very plentiful; abundant. copious.
	\textcolor{gold}{"I offered my profuse apologies" "Wild dogs, which could be found there in profuse numbers." "The connoisseur was able to glean a worthwhile painting from the profuse variety of poor ones at the exhibit."}
	
	\subsubsection{\textcolor{brickred}{dulcet} (adj) [duhl·suht]}
	(especially of sound) sweet and soothing (often used ironically). sweet or \underline{melodious} (harmonious, melodic) to the ear.
	\textcolor{gold}{"The dulcet song of the wild birds \textbf{whetted} the interest of the captain." "record the dulcet tones of your family and friends" "The blasé \textbf{devotee} (enthusiast fan) of the opera was awakened from his ennui by the dulcet tones of the new soprano."}
	
	\subsubsection{\textcolor{brickred}{impromptu} (adj)}
	done without being planned, organized, or rehearsed. offhand.
	\textcolor{gold}{"In impromptu cages hundreds were taken aboard to be traded." "an impromptu press conference" "As the music reached a \textbf{frenetic} tempo, the audience \textbf{lost all decorum} and broke into impromptu dancing."}
	
	\subsubsection{\textcolor{brickred}{malevolent} (adj)}
	having or showing a wish to do evil to others. malicious, spiteful, hostile.
	\textcolor{gold}{"the \textbf{glint} (shine) of dark, malevolent eyes" "As they approached the island of Elba, near Italy, a malevolent storm put the boat in jeopardy of sinking." "He had no qualms about opposing the clique who insidiously \textbf{exerted} (apply or bring to bear (a force, influence, or quality)) a malevolent influence on the president."}
	
	\newpage
	\setcounter{section}{45}
	\setcounter{subsection}{0}
	
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{wistful} (adj)}
	having or showing a feeling of vague or \underline{regretful} \underline{longing}. nostalgic, yearning [yur·nuhng]. rueful. pensive.
	\textcolor{gold}{"Do you get wistful when you recall the romantic tales that begin with an innocent maiden traveling through the rustic countryside?" "a wistful smile" "To be candid, there is little to be wistful about in the "good old days.""}
	
	\subsubsection{\textcolor{brickred}{raiment} (n) [rei·muhnt]}
	clothing. (=jaameh)
	\textcolor{gold}{"ladies clothed in raiment \textbf{bedeck}ed (=== decorate) with jewels" "She is dressed in \textbf{glittering} raiment." "The potpourri of au courant fashionable raiment includes the fatuous and the discreet."}
	
	\subsubsection{\textcolor{brickred}{brigand} (n) [bri·gnd]}
	bandit,
	robber,
	outlaw.
	\textcolor{gold}{"The scene is idyllic. Without warning, the group is set upon by a \textbf{virile} brigand" "They captured the brigand, and he was incarcerated for a mandatory period."}
	
	\subsubsection{\textcolor{brickred}{corpulent} (adj) [kor·pyuh·luhnt]}
	(corpulence) fat. plump, portly, stout, chubby, paunchy.
	\textcolor{gold}{"Her corpulent escort is irate, but unable to do anything to thwart this debacle." "Is there any \textbf{veracity} in the platitude that corpulent men are jocose?" "a short, somewhat corpulent man"}
	
	\subsubsection{\textcolor{brickred}{rail} (v)}
	complain/protest strongly and persistently about. \textbf{fulminate}/inveigh against.
	\textcolor{gold}{"he \textbf{railed at} human fickleness" "While all disgruntled men may \textbf{rail against} malevolent or Machiavellian leaders, democracy offers a way \textbf{to ameliorate iniquities} through the \textbf{ballot}."}\\\\
	- Pandemonium results! Her entourage is in a state of bedlam.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{raconteur} (n) [ra·kuhn·tur]}
	a skilled \underline{storyteller}.
	\textcolor{gold}{"Well known as a raconteur , he was never \textbf{chagrin}ed when asked to tell a sto:ty from his large repertoire." "The raconteur of our story about idyllic times gone by goes on to \textbf{elucidate} how the comely heroine is taken to the bandits' hideout." "a colorful raconteur"}
	
	\subsubsection{\textcolor{brickred}{sullen} (adj)}
	bad-tempered and \underline{sulky}; gloomy. surly. aboos.
	\textcolor{gold}{"Despite all attempts to mollify her, she remained sullen about the \textbf{levity} caused by her \textbf{slovenly} raiment." "There, a sullen crew of cutthroats is gathered." "a sullen \textbf{pout}"}
	
	\subsubsection{\textcolor{brickred}{rift} (n)}
	a serious break in friendly relations. split, falling-out.
	\textcolor{gold}{"their demise caused a rift between the city's town and gown" "There is a rift among the criminals. Their leader remains \textbf{truculent}." "He alluded to the rift caused in the school by the plethora of hirsute boys who ignored the criterion for appearance."}
	
	\subsubsection{\textcolor{brickred}{emissary} (n)}
	agent, envoy, ambassador. a person sent on a special mission, usually as a diplomatic representative.
	\textcolor{gold}{"The obscure country, an \textbf{aspirant} for membership in the United Nations, sent an emissary." "An emissary from the grief-stricken parents is expected at any moment."}
	
	\subsubsection{\textcolor{brickred}{ruminate} (v)}
	VA 262. contemplate, mull over,
	meditate on,
	pore/muse on,
	ponder on/over.
	\textcolor{gold}{"we sat \textbf{ruminating on} the nature of existence" "The wan maiden, her spirits at their nadir, has time to \textbf{ruminate about} her lugubrious fate."}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{taut} (adj) [taat]}
	 tense; not relaxed. keyed up, on edge
	\textcolor{gold}{"my voice was taut with anger" "Back at the castle, the situation is taut with emotion." "There was a taut international situation caused by the proximity of unidentified submarines to our coasts."}
	
	\subsubsection{\textcolor{brickred}{\hl{livid}} (adj)}
	($\neq$ lurid) 1- \underline{furious}ly \underline{angry}. infuriated, irate, fuming, raging, seething, incensed, enraged, beside oneself, wrathful, ireful.
	2- dark bluish gray in color. pale.
	\textcolor{gold}{"he was livid at being left out" "livid bruises" "The fair maiden's mother is livid with fear and anxiety; she has attacks of vertigo." "The rabid baseball fan lost his equanimity and became livid when the star pitcher became pugnacious and was removed from the game."}
	
	\subsubsection{\textcolor{brickred}{martinet} (n)}
	VA 371. a strict \underline{disciplinarian}.
	\textcolor{gold}{"the woman in charge was a martinet who treated all those beneath her like children" "The girl's father, a martinet who rules his family with an iron hand, \textbf{staunchly} refuses to pay the ransom. Iniquity shall not be rewarded!" "When one enlists in the army, one expects to be under the aegis of a martinet"}
	
	\subsubsection{\textcolor{brickred}{yen} (n/v)}
	a longing or yearning. hankering. itch.
	\textcolor{gold}{"the continuing boom in the economy is allowing many consumers to indulge their yen for high-end toys" "At this moment of crisis a heroic knight volunteers to rescue our heroine; he has had a secret yen for the young beauty." "His yen for imbibing and romping with girls worked to his detriment."}
	
	\subsubsection{\textcolor{brickred}{bagatelle} (n) [ba·guh·tel]}
	a trifle, a thing of little importance; a very easy task.
	\textcolor{gold}{"dealing with these boats was a mere bagatelle for the world's oldest yacht club" "He holds his life as a mere bagatelle against the duty he owes his beloved mistress. At the propitious moment, he rides off to do or die for her." "The little boy tried to wheedle a larger allowance from his father by the caustic observations that it was a mere bagatelle when compared to the allowances of his friends."}\\\\
	- Avoiding rhetoric, he pledges his all to castigate those responsible for this ignominious deed.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{callow} (adj)}
	VA 151. KHAAM, (of a young person) inexperienced and immature. naive.
	\textcolor{gold}{"earnest and callow undergraduates" "Despite his callow appearance, he is reputed to..." "It was deplorable the way the capricious girl \textbf{led} the callow youth on \textbf{a merry chase}."}
	
	\subsubsection{\textcolor{brickred}{appalled} (adj)}
	(appall) greatly dismayed or horrified.
	\textcolor{gold}{"Alison looked at me, appalled" "They are appalled at the prospect, and they are in a quandary as to which one will meet him on the field of combat." "Each long holiday weekend we are appalled at the carnage on our highways."}
	
	\subsubsection{\textcolor{brickred}{penchant} (n)}
	VA 94.
	\textcolor{gold}{"he has a penchant for adopting stray dogs" "The leader, under duress, rides out. "Do you have a penchant to die?" derides the knight. More vituperative remarks follow." "I do not wish to deprecate your penchant for cowboy music, but I find it banal."}
	
	\subsubsection{\textcolor{brickred}{decapitate} (v)}
	behead,
	guillotine,
	decollate.
	\textcolor{gold}{"We do not decapitate criminals because of our aversion to such repugnant punishments." "It takes \textbf{but one} swift blow for our hero to decapitate the villain."}
	
	\subsubsection{\textcolor{brickred}{termagant} (n) [tur·muh·gnt]}
	a harsh-tempered/overbearing/scolding woman. a shrew. a virago. a harridan.
	\textcolor{gold}{"Little does the knight realize that the fair maiden is a garrulous termagant who will make his life miserable with caustic remarks. =D" "Why do you remain docile while that termagant besmirches, maligns, and belittles you?"}\\\\
	- \textbf{lurid}: week 11
	
	\newpage
	\setcounter{section}{46}
	\setcounter{subsection}{0}
	
	\subsection{}
	\subsubsection{\textcolor{brickred}{ascertain} (v)}
	\underline{find} (sth) \underline{out} for certain; make sure of. discover.
	\textcolor{gold}{"an attempt to ascertain the cause of the accident" "but we do not \textbf{feel it incumbent upon us} to ascertain anything about the civilizations in our own hemisphere." "In order to ascertain the relationship between his girlfriend and his brother, \textbf{he kept a wary and discreet vigil.}"}
	
	\subsubsection{\textcolor{brickred}{dormant} (adj)}
	asleep, resting, temporarily inactive or inoperative.
	\textcolor{gold}{"that dormant urge to write fiction has re-emerged" "dormant butterflies" "the disease may remain dormant and undetected until transmitted to other fish" "...as though progress lay dormant" "He was appalled at the apathy concerning the important issue that had remained dormant for so long a time"}
	
	\subsubsection{\textcolor{brickred}{\hl{burgeon}} (v) [bur·jn]}
	grow/increase rapidly; flourish. expand.
	\textcolor{gold}{"This civilization is reputed to have burgeoned until it covered more than 2,500 miles of the western part of the continent." "the city's suburbs have burgeoned, sprawling out from the centre" "While \textbf{some moribund economies atrophied after World War II}, others burgeoned under the salubrious effects of loans from the U.S."}
	
	\subsubsection{\textcolor{brickred}{potentate} (n) [pow·tuhn·teit]}
	a monarch or ruler, especially an autocratic one. sovereign.
	\textcolor{gold}{"Its potentate ruled with absolute power (autocracy)." "\textbf{The callous potentate kept an imperturbable mien} when requested to alleviate the unconscionable conditions existing in his land."}
	
	\subsubsection{\textcolor{brickred}{disseminate} (v)}
	spread widely. (especially information)
	\textcolor{gold}{"health authorities should \textbf{foster} (= encourage) good practice by disseminating information" "As the empire conquered new lands, it would disseminate its language, religion, and social customs." "We are quick to disseminate calumny, but reticent about things that may be construed as compliments."}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{derive} (v) [duh·raiv]}
	\underline{obtain} something from (a specified source).
	\textcolor{gold}{"they derived great comfort from this assurance" "The Inca emperor derived his prodigious power and authority from the gods."}
	
	\subsubsection{\textcolor{brickred}{\hl{prerogative}} (n) [pr·aa·guh·tuhv]}
	a \underline{right} or privilege exclusive to a particular individual or class. entitlement.
	\textcolor{gold}{"in some countries, higher education is predominantly the prerogative of the rich" "the ruler passed on his prerogative to rule to his most astute son." "He gave his adversary the dubious prerogative of choosing the weapon by which he was to meet his inevitable end."}
	
	\subsubsection{\textcolor{brickred}{nepotism} (n)}
	VA 337.
	\textcolor{gold}{"\textbf{Your efforts to ingratiate yourself into your boss's favor are nullified by the unmitigated nepotism manifest in this firm.}"}
	
	\subsubsection{\textcolor{brickred}{dearth} (n)}
	VA 98.
	\textcolor{gold}{"In the potpourri of restaurants there is no dearth of succulent dishes."}
	
	\subsubsection{\textcolor{brickred}{internecine} (adj) [in·tr·neh·seen]}
	1- destructive to both sides in a conflict. (mutually destructive) 2- involving/relating to conflict within a group.
	\textcolor{gold}{"The emissary from the president tried \textbf{to allay the} fears that a deleterious internecine feud was inevitable within the party." "In 1528 two sons began an internecine struggle for control which resulted in civil war." "the region's history of savage internecine warfare" "the party shrank from the trauma of more internecine strife"}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{tyro} (n)}
	VA. 136. beginner, novice, neophyte, greenhorn.
	\textcolor{gold}{"Overwhelmed with cupidity, but still a tyro when it came to \textbf{wresting} power and wealth from hapless people, he joined with an inveterate adventurer." "Although he was erudite about a copious number of things, he was a naive, callow tyro when it came to relating to girls."}
	
	\subsubsection{\textcolor{brickred}{sophistry} (n)}
	VA 143.
	\textcolor{gold}{"Whether by sophistry or cajolery, he was given the requisite aid." "trying to argue that I had benefited in any way from the disaster was pure sophistry" "Her sophistry made use of every glib artifice."}
	
	\subsubsection{\textcolor{brickred}{factitious} (adj)}
	VA 467. ($\neq$ facetious, fatuous) sham.
	\textcolor{gold}{"In the office he played the factitious role of a martinet, while at home he was filled with compassion" "a largely factitious national identity"}
	
	\subsubsection{\textcolor{brickred}{encomium} (n)}
	eulogy, a speech or piece of writing that praises someone or something highly. praise, panegyric [pa·nuh·jee·ruhk], paean, extolment,
	laudation.
	\textcolor{gold}{"The modest prodigy treated the fervid encomium that followed his performance as though they were a mere bagatelle." "The Incas welcomed Pizarro who, in  a factitious display of friendship, heaped encomiums upon them."}
	
	\subsubsection{\textcolor{brickred}{obloquy} (n)}
	1- VA 320. strong public condemnation.\\
	2- disgrace, shame, dishonor. especially that \textbf{brought about by} public condemnation.
	\textcolor{gold}{"conduct to which no more obloquy could reasonably attach" "The obloquy of his next act, ambushing the Incas and taking Atahualpa prisoner, will live in  the history books that are replete with tales of conquest." "John's egregious act remains an infamous obloquy" "he endured years of contempt and obloquy"}\\\\
	- \textbf{to hold court} = be the centre (= center) of attention amid(st) a crowd of one's admirers.
	"Lewis was holding court in the small dressing room"\\
	- With a force of 180 men, the dregs of society, he invaded Inca territory.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{hyperbole} (n)}
	VA 341. exaggeration, overstatement, magnification, amplification, embroidery, embellishment.
	\textcolor{gold}{"he vowed revenge with oaths and hyperboles" "The rhetoric \textbf{soared} (fly or rise high in the air. increase rapidly above the usual level.) into flagrant hyperbole"}
	
	\subsubsection{\textcolor{brickred}{munificent} (adj)}
	VA 406 (munificence).
	\textcolor{gold}{"This was taken as a hyperbole at first, but Pizarro knew the gullible Incas would be munificent when it came to rescuing their sacred ruler." "a munificent bequest (legacy, inheritance)" "He was surprised by the munificent gratuity given by the usually parsimonious termagant."}
	
	\subsubsection{\textcolor{brickred}{prevarication} (n)}
	prevaricate (v): speak or act in an evasive way.
	\textcolor{gold}{"he seemed to prevaricate when journalists asked pointed questions" "Pizarro, to whom prevarication was natural in dealing with the Incas, had no qualms about executing their ruler as soon as he had the gold." "Her constant prevarication made her a pariah to her friends."}
	
	\subsubsection{\textcolor{brickred}{charisma} (n)}
	compelling attractiveness or \underline{charm} that can inspire devotion in others.
	\textcolor{gold}{"he has tremendous charisma and stage presence" "The Inca empire was moribund, but the charisma that surrounded Atahualpa was such that, after his death, the Incas fought on tenaciously in his name for several years."}
	
	\subsubsection{\textcolor{brickred}{genocide} (n)}
	ghatle aam. the deliberate killing of a large number of people from a particular nation or ethnic group with the aim of destroying that nation or group. massacre.
	\textcolor{gold}{"Eventually, superior weapons quelled all opposition. A policy of genocide was adopted by the Spanish conquerors, and almost two million of these proud people died in the carnage that followed." "a campaign of genocide"}\\\\
	- They did not procrastinate, and a frenetic collection of gold took place.
	
	\newpage
	\setcounter{section}{46}
	\setcounter{subsection}{0}
	
	\section{BONUS WEEK A}
	\subsection{}
	\subsubsection{\textcolor{brickred}{impregnable} (adj) [uhm·preg·nuh·bl]}
	1- unable to be captured or broken into. impenetrable. 2- unable to be defeated or overcome. unassailable.
	\textcolor{gold}{"A company of marines was unable to penetrate the seemingly impregnable fortress." "Liverpool used their good fortune to forge an impregnable lead" "the story of the allegedly impregnable Titanic, the unsinkable majestic ocean liner that tumbled to the bottom of the icy Atlantic waters with 1600 passengers still aboard."}
	
	\subsubsection{\textcolor{brickred}{toxic} (adj)}
	virulent, also very harmful/unpleasant in a pervasive or insidious way.
	\textcolor{gold}{"the dumping of toxic waste" "Coal miners are often subject to toxic fumes/hazards" "a toxic relationship" "How could such a toxic tragedy have occurred?"}
	
	\subsubsection{\textcolor{brickred}{patriarch} (n) [pei·tree·aark]}
	the male head of a family or tribe. an older man who is powerful within an organization. the male founder of sth.
	\textcolor{gold}{"How could the naval patriarch, Captain Edward Smith, \textbf{no neophyte he}, have allowed the disaster to happen?" "Hollywood's reigning patriarch rose to speak" "he's the patriarch of all spin doctors" "Grandfather is the recognized patriarch of our family."}
	
	\subsubsection{\textcolor{brickred}{neophyte} (n)}
	VA 136.
	\textcolor{gold}{"four-day cooking classes are offered to neophytes and experts" "a neophyte at computers."}
	
	\subsubsection{\textcolor{brickred}{exte\underline{nua}ting} (adj)}
	\textbf{extenuate} (v): cause (an offence/offense) to seem less serious.
	\textcolor{gold}{"library staff will waive fines where there are genuine \textbf{extenuating circumstances}" "even the fact that you once helped to save my life could not extenuate your offence" "What were the extenuating circumstances that led to the death of that glorious White Star queen?" "Robert's defense lawyer pointed out the extenuating conditions of the case."}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{foreboding} (n)}
	a feeling that something bad will happen; fearful \underline{apprehension}. premonition, trepidation
	\textcolor{gold}{"Caesar's wife had forebodings about the danger facing her husband." "with a sense of foreboding she read the note" "Next came the German Amerika, echoing the same forebodings"}
	
	\subsubsection{\textcolor{brickred}{em\underline{a}nate} (v) [eh·muh·neit]}
	originate/coming from; be produced by.
	\textcolor{gold}{"All the messages emanating from sister ships should have had a profound effect on Smith and company. " "the proposals emanated from a committee" "warmth emanated from the fireplace" "he emanated a powerful \textbf{brood}ing air" "The rulings emanated from the local court were cheered by the conservatives."}
	
	\subsubsection{\textcolor{brickred}{miscreant} (adj/n)}
	VA 370.
	\textcolor{gold}{"the police are straining every nerve to bring the miscreants to justice" "his miscreant wife" "No one miscreant could be \textbf{finger}ed (identify, select :D), but \textbf{a host of} crew members were certainly blameworthy." "The class miscreant"}
	
	\subsubsection{\textcolor{brickred}{protocol} (n)}
	\textcolor{gold}{"protocol forbids the prince from making any public statement in his defence/defense" "what is the protocol (conventions, decorum) at a smart lunch if one's neighbour dozes off during the speeches?" "There was no standard protocol for the handling of such messages." "Failing to follow protocol got Sophia into trouble at the office."}
	
	\subsubsection{\textcolor{brickred}{circuitous} (adj) [sr·kyoo·i·tuhs]}
	roundabout, winding, meandering, serpentine, tortuous, twisting, anfractuous, oblique, circumlocutory, periphrastic. (of a route or journey) longer than the most direct way.
	\textcolor{gold}{"Captain Smith would certainly have taken a circuitous route so as to avoid the dangerous icebergs."}\\\\
	- On the following day, \textbf{there came a spate of} other warnings from a Cunard ship.\\
	- Notations were indeed made on slips of paper but largely ignored and forgotten.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{knell} (n/v) [nel]}
	toll, the sound of a bell, especially when rung solemnly for a death or funeral. (BAANG)
	\textcolor{gold}{ "DEATH KNELL FOR THE TITANIC"}
	
	\subsubsection{\textcolor{brickred}{macabre} (adj) [muh·kaab]}
	gruesome, disturbing because concerned with/causing a fear of death.
	\textcolor{gold}{"a macabre series of murders" "There followed a macabre scene as the ship's band, \textbf{clad} {clothed} \textbf{in their tuxedos}, continued to play show tunes while hordes of terrified passengers, many in nightclothes, rushed toward the lifeboats." "The bloody macabre scenes in a movie"}
	
	\subsubsection{\textcolor{brickred}{ramification} (n)}
	a complex/unwelcome \underline{consequence} of an action/event. complication.
	\textcolor{gold}{"The crew called out, "Women and children first," but their lack of an orderly plan for loading would have profound ramifications" "any change is bound to have legal ramifications" "Heidi was concerned about the ramifications of her employer's new policy."}
	
	\subsubsection{\textcolor{brickred}{rapacious} (adj) [ruh·pei·shuhs]}
	aggressively \underline{greedy} or \underline{grasping}. avaricious, acquisitive, covetous.
	\textcolor{gold}{"As panic began to take hold, the realization that there weren't enough lifeboats \textbf{exacerbate}d the situation, bringing out the worst in \textbf{a rapacious few}." "rapacious landlords"}
	
	\subsubsection{\textcolor{brickred}{insurgent} (adj/n)}
	rebellious, rising in active revolt.
	\textcolor{gold}{"alleged links with insurgent groups" "a series of insurgent attacks" "an attack by armed insurgents" "Several insurgent males ignored the crew and jumped into descending lifeboats. It was an act of shame they would have to live with for the rest of their lives." "Additional troops were dispatched to deal with the insurgent threat."}\\\\
	- Within seconds, thousands of cubic feet of water had penetrated the shattered hull.\\
	- (\textbf{grisly} $\neq$ grizzly)\\
	- the ramifications of a failure to control the high blood sugar
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{glut} (n/v)}
	an \underline{excess}ively abundant supply of sth. surplus, surfeit, superfluity, overabundance.
	\textcolor{gold}{"The glut of billionaires on board" "there is a glut of cars on the market" "the roads are glutted with cars" "Our choir has a glut of tenors and a shortage of sopranos."}
	
	\subsubsection{\textcolor{brickred}{risible} (adj)}
	VA 455.
	\textcolor{gold}{"a risible scene of lovemaking in a tent" "The average claim had been for a modest \$1500, and the average award, paid by the White Star Line, was a risible \$1000."}
	
	\subsubsection{\textcolor{brickred}{dilatory} (adj)}
	VA 422.
	\textcolor{gold}{"he had been dilatory in appointing a solicitor" "White Star's top notch legal staff was accused of using dilatory tactics, \textbf{tiring the claimants} until they agreed to settle for a  mere pittance." "they resorted to dilatory tactics, forcing a postponement of peace talks"}
	
	\subsubsection{\textcolor{brickred}{specious} (adj)}
	VA 424.
	\textcolor{gold}{"Their lawyers called many claims specious and rejected them \textbf{out of hand} (= without taking time to think)." "a specious argument" "the music trade gives Golden Oldies a specious appearance of novelty"}
	
	\subsubsection{\textcolor{brickred}{denouement} (n) [dei·noo·maan]}
	VA 417.
	\textcolor{gold}{"the film's denouement was unsatisfying and ambiguous (equivocal, ambivalent)" "The denouement of the story is rather sad." "The play's denouement came with three dead bodies on the stage."}\\\\
	- American and British \textbf{maritime} law had long given special protection to ship owners \textbf{on the grounds that} their business was such a risky one.\\
	- omen: an event regarded as a \textbf{portent} of good or evil.
	
	\newpage
	\setcounter{section}{47}
	\setcounter{subsection}{0}
	
	\section{BONUS WEEK B}
	\subsection{}
	\subsubsection{\textcolor{brickred}{dolorous} (adj)}
	doleful, woeful, dismal, forlorn. feeling or expressing great sorrow or distress.
	\textcolor{gold}{"a dolorous and repetitive tale of atrocity" "The dolorous Civil War that had crippled the young nation was finally over." "We were surprised when Ted's happy expression turned into a dolorous one."}
	
	\subsubsection{\textcolor{brickred}{enervate} (v)}
	exhaust, tire, fatigue, weary (v), wear out, devitalize, sap, enfeeble, debilitate, incapacitate, \textbf{prostrate} (as a verb basically means ZAMINGIR SHODAN/KARDAN).
	\textcolor{gold}{"the heat enervated us all" "The burden of being a wartime president had so enervated Lincoln that Surgeon General Barnes feared an imminent nervous breakdown." "Daniel felt too enervated (\textbf{adj}) to resist" "Enervated by his long walk, Jose \textbf{took to his bed}."}
	
	\subsubsection{\textcolor{brickred}{suffrage} (n)}
	the right to vote in political elections.
	\textcolor{gold}{"universal adult suffrage" "He advocated the granting of suffrage to Negro soldiers." "The dictator lied when he claimed he favored suffrage for women."}
	
	\subsubsection{\textcolor{brickred}{cabal} (n)}
	a secret political \underline{clique} or \underline{faction}. coterie. secret group of plotters.
	\textcolor{gold}{"a cabal of dissidents" ""'That's the last speech he will ever make," said Booth to a fellow member of \textbf{his cabal of conspirators}." "The members of the revolutionary cabal were arrested and jailed."}
	
	\subsubsection{\textcolor{brickred}{odious} (adj)}
	VA 261. extremely unpleasant; repulsive.
	\textcolor{gold}{"Booth's odious plan was to assassinate Lincoln whom he hated passionately, while an associate, would do the same to Vice-President Andrew Johnson." "Sylvia's odious remarks caused the audience to turn against her." "a pretty odious character"}\\
	- The rapacious dictator used guile to achieve his goals.\\
	- "We have had \textbf{a glut of dilatory} tactics," the judge declared, "and I will not put up with it."
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{prescient} (adj) [preh·shee·uhnt]}
	having or showing knowledge of events before they take place. prophetic, psychic, clairvoyant.
	\textcolor{gold}{"a prescient warning" "Lincoln's family remembered that the President had a prescient dream in March, several weeks before the fatal day, and provided them with a \textbf{verbatim} account." "Claiming to be prescient, the fortune teller took advantage of the gullible woman."}
	
	\subsubsection{\textcolor{brickred}{verbatim} (adv/adj) [vr·bei·tm]}
	(adv) word for word, in exactly the same words as were used originally.\\
	(adj) copied, quoted, or translated in exactly the same words as were used originally.
	\textcolor{gold}{"subjects were instructed to recall the passage verbatim (adv)" "a verbatim account" "With remarkable talent, the reporter was able to quote speeches verbatim"}
	
	\subsubsection{\textcolor{brickred}{reverie} (n) [reh·vr·ee]}
	a state of being pleasantly lost in one's thoughts; a daydream. trance, fantasy.
	\textcolor{gold}{"a knock on the door broke her reverie" "In his reverie, Lincoln asked a soldier, "Who is dead in the White House?"" "In her reverie, Ellen saw herself as the next U.S. President."}
	
	\subsubsection{\textcolor{brickred}{thespian} (n/adj) [theh·spee·uhn]}
	an actor/actress.
	\textcolor{gold}{"an aging thespian" "thespian talents" "As a thespian, he romanticized the action that he could take to rid the nation of a cruel \textbf{warmonger}." "Yearning to be a thespian, Roger took lessons from a dramatic coach."}
	
	\subsubsection{\textcolor{brickred}{despot} (n)}
	tyrant, dictator, absolute ruler, totalitarian, authoritarian, \textbf{autocrat}.
	\textcolor{gold}{"he could contribute to the Confederate cause by kidnapping the bearded despot." "When he lost control of the militia, the despot was forced to flee."}
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{pathological} (adj)}
	($\neq$ IATROGENIC) pertaining to or caused by disease (mental or physical)
	\textcolor{gold}{"glands with a pathological abnormality" "The defense lawyer admitted that his client was a pathological liar."}
	
	\subsubsection{\textcolor{brickred}{articulate} (adj)}
	eloquent, communicative, having/showing the ability to speak \underline{fluent}ly and \underline{coherent}ly.
	\textcolor{gold}{"an articulate account of their experiences" "The \textbf{pathological} yet articulate Booth had rounded up several co-conspirators and shared his delusions of \textbf{grandeur} with them." "Hal was surprisingly articulate for a  high school freshman."}
	
	\subsubsection{\textcolor{brickred}{grandeur} (n) [gran·jr]}
	magnificence, splendor and impressiveness, especially of appearance/style.
	\textcolor{gold}{"the majestic grandeur and simplicity of Roman architecture" "In history class, we studied the grandeur of Greece and the glory of Rome."}
	
	\subsubsection{\textcolor{brickred}{polemic} (n) [puh·leh·muhk]}
	a strong verbal/written attack on sb/sth.
	\textcolor{gold}{"his polemic against the cultural relativism of the Sixties" "He had produced a polemic that convinced his crew that it would be a patriotic thing to capture the President." "The team captain's polemic led to a fist fight in the locker room."}
	
	\subsubsection{\textcolor{brickred}{impasse} (n) [im·pas]}
	a \textbf{deadlock}. a situation in which no progress is possible, especially because of disagreement.
	\textcolor{gold}{"the current political impasse" "Several \textbf{dry runs} had not worked out for them who were about to reach an impasse" "The impasse was broken when the union concurred to management's offer."}\\\\
	- to ferry across a river.
	
	\newpage
	\subsection{}
	\subsubsection{\textcolor{brickred}{regimen} (n) [reh·juh·muhn]}
	\textcolor{gold}{"a regimen of one or two injections per day" "Aunt Ethel's morning regimen called for three cups of coffee." "as regimen dictated, the band played "Hail to the Chief.""}
	
	\subsubsection{\textcolor{brickred}{denigrate} (v)}
	criticize unfairly; disparage. deprecate.
	\textcolor{gold}{"doom and gloom merchants who denigrate their own country" "Booth said to a drunk who had denigrated his acting skill, "Nigga, Fuck you."" "When her boss denigrated Martha's stenographic ability, she quit."}
	
	\subsubsection{\textcolor{brickred}{guile} (n)}
	VA 216. sly/\underline{cunning} intelligence. craftiness, craft, artfulness, deception, deceit, duplicity, underhandedness, double-dealing, treachery, chicanery.
	\textcolor{gold}{"he used all his guile and guts to free himself from the muddle he was in" "At about 10 P.M., with extreme guile, Booth had managed to be behind Box 7 in the darkness of the hallway." "Using guile, the magician pulled the wool over the spectators' eyes."}
	
	\subsubsection{\textcolor{brickred}{mortal} (adj)}
	fatal, lethal.
	\textcolor{gold}{"it was apparent that a mortal wound had been \textbf{inflicted}, and he could not be saved." "a mortal disease" "The blow to the boxer's Jaw turned out to be a mortal one."}
	
	\subsubsection{\textcolor{brickred}{inflict} (v)}
	impose. cause (sth unpleasant/painful) to be suffered by sb/sth.
	\textcolor{gold}{"they inflicted serious injuries on three other men" "she is wrong to inflict her beliefs on everyone else" "The prison guards inflict torture on some of the inmates."}\\\\
	- He saw the silhouette of a head above the horsehair rocker.\\
	- he \textbf{host} of perks they offer reflect the guile behind their generosity.\\
	- \textbf{invigorate}: "the shower had invigorated her" "Our employees work hard and can become enervated," said a Serus executive, "and we want to invigorate them with sky dives, as well as cruises"
	
\end{document}